---
title: "University of Chicago - COVID-19 Biobank - Analysis"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

# Initial setup
- Importing packages

```{r Setup}
########################
#     KNIT OPTIONS     #
########################

knitr::opts_chunk$set(echo = TRUE)

########################
#      LIBRARIES       #
########################

library(tidyverse)
library(reticulate)
library(gridExtra)
library(patchwork)
library(ggpmisc)
library(ggpubr)
library(ggsignif)
library(lubridate)
library(stringr)
library(survival)
library(Formula)
library(zoo)
library(scales)
library(rstatix)
```

# Importing REDCap Data, setting global variables
- Utilizing R script from REDCap export, taking most recently modified version.
- Long list of specific inclusion/exclusion criteria from separate Excel sheet

```{r REDCap}
########################
#        REDCAP        #
########################
rm(list = ls())

STR_CODE_DIR_REDCAP <- "code/redcap"

# Setting working directory (both for running in knitr and in RStudio)
#knitr::opts_chunk$set(root.dir = STR_CODE_DIR_REDCAP )
#setwd(STR_DATA_DIR_REDCAP)

# Uses REDCap provided script on export, requires installation of Hmisc (Harrell Miscellaneous)
# Unfortunately, when sourcing this script, all workspace variables are cleared
str_redcap_r <- list.files(path = STR_CODE_DIR_REDCAP,
           pattern = "COVID19Biobank.*r$",
           full.names = TRUE) %>%
  magrittr::extract(which.max(file.mtime(.)))
list_str_r_file <- readLines(str_redcap_r)
list_str_r_file_fixed <- gsub("data=read.csv\\('COVID19", "data=read.csv\\('data\\/redcap\\/COVID19", list_str_r_file)
cat(list_str_r_file_fixed, file=str_redcap_r, sep="\n")

source(str_redcap_r)

# Reformatting dataframe into tibble, standardizing MRN format
tib_redcap <- data %>%
  as_tibble() %>%
  mutate(
    mrn = str_replace(as.character(mrn), " ", ""),
    id = as.character(record_id),
    death_date = ymd(death_date)
  )

# Cleanup
rm(data)
# rm(str_redcap_r)
# rm(STR_CODE_DIR_REDCAP)

########################
#   GLOBAL VARIABLES   #
########################

# Folders where files are being stored
# `STR_BIOBANK`: Biobank data on Box from rest of lab
# `STR_BIOBANK_DATAMART_RAW`: Current version of DataMart
# `STR_BIOBANK_DATAMART`: Location to place the preprocessed/cleaned DataMart
# `STR_BIOBANK_DEMO`: Demographic data in the Datamart
STR_BIOBANK <- "../../COVID-19 Biobank/"
STR_BIOBANK_DATAMART_RAW <- "Datamart/Datamart 08122020/"
STR_BIOBANK_DATAMART <- "Datamart/data-preprocessed 08122020/"
STR_BIOBANK_DEMO <- "Demographics, controls, ect"

STR_DATA_DIR_DEMO_CLIN <- "data/demographics_clinical/"
STR_DATA_DIR_CYTOKINE <- "data/cytokine/"
STR_DATA_DIR_FLOW <- "data/flow/"
STR_DATA_DIR_ELISA <- "data/elisa/"
STR_DATA_DIR_OTHER <- "data/other/"

STR_PLOT_DIR_CLINICAL <- "output/clinical/"
STR_PLOT_DIR_CYTOKINE <- "output/cytokine/"
STR_PLOT_DIR_FLOW <- "output/flow/"
STR_PLOT_DIR_ELISA <- "output/elisa/"
STR_PLOT_DIR_OTHER <- "output/other/"

STR_CODE_DIR_DATAMART <- "code/datamart/"
STR_CODE_DIR_CYTOKINE <- "code/cytokine/"

fun_significance <- function(x){
  case_when(
    x < 0.0001 ~ "****",
    x < 0.001 ~ "***",
    x < 0.01 ~ "**",
    x < 0.05 ~ "*",
    TRUE  ~ "ns",
  ) %>%
    return()
}

INT_SIG_SIZE = 3

INT_FIG_WIDTH = 4
INT_FIG_HEIGHT = 4

# Defining SF ratio groups and cut/break points
SF_BREAKS <- c(-1, 234, 314, Inf)

sflevels <- function(healthy = FALSE, rev = FALSE) {
  levels <- c("Severe", "Moderate", "Mild")
  if (healthy) {
    levels = c(levels, "Healthy")
  }
  if (rev) {
    return(rev(levels))
  }
  else (
    return(levels)
  )
}

plotcolors <- function(rev = FALSE, sfmatch = FALSE, int_n = 4) {
  colors <- c(
    "#f03b20", #Red
    "#feb24c", #Orange
    "#a1d99b", #Green
    "#9ecae1" #Blue
  )
  if(sfmatch != FALSE) {
    colors <- as.list(colors)
    names(colors) <- sflevels(TRUE)
    colors <- colors[sfmatch] %>%
      unlist() %>%
      as.vector()
  }
  else {
    if(int_n == 2) {
      colors <- colors[c(2,4)]
    }
    else {
      colors <- colors[1:int_n]
    }
  }
  if(rev) {
    colors <- rev(colors)
  }
  return(colors)
}

tib_columns <- readxl::read_xlsx("data_columns.xlsx", col_names = c("keep", "variable", "name", "mod", "category"), sheet = 1) %>%
  separate(keep, c("keep", "merge"), sep = ":", fill = "right")
tib_columns <- tib_columns %>%
  left_join(tib_columns %>% select(variable, parent_name = name), by = c("merge" = "variable")) %>%
  mutate(
    max = grepl("max", mod, ignore.case = TRUE),
    min = grepl("min", mod, ignore.case = TRUE),
    mean = grepl("mean", mod, ignore.case = TRUE),
    first = grepl("first", mod, ignore.case = TRUE),
    keep = !grepl("drop", keep, ignore.case = TRUE),
    name = case_when(
      !keep ~ "",
      !is.na(parent_name) ~ parent_name,
      name == "0" ~ variable,
      TRUE ~ name
    )
  ) %>%
  filter(keep) %>%
  select(-keep)

```

# Setting up COVID-19 DataMart data import
- Adapted from previous project with REACT COVID-19 through Swedish to accommodate identified data˜
- Cleaning text files due to bizarre encoding issues from CRI using Python just because it's way easier than R for basic text manipulation
-- Using last modified time of the DataMart to minimize need for reprocessing every time this is run

```{r Datamart}
########################
#   DATAMART: BASICS   #
########################

# Run python script if the data is new
if(file.info(paste0(STR_BIOBANK, STR_BIOBANK_DATAMART_RAW, "C19_ENC_XTRA_GAJEWSKI", ".txt"))$mtime >
    file.info(paste0(STR_BIOBANK, STR_BIOBANK_DATAMART, "C19_ENC_XTRA_GAJEWSKI", ".txt"))$mtime ) {
  string <- py_capture_output(py_run_file(paste0(STR_CODE_DIR_DATAMART, "datamartPreprocess.py")))
}

# Function for data import to specify column types from above, specify NA values
fun_import_data <- function( str_filename ) {
  # A list of files in the DataMart with specific column type specifications to minimize issues with read_delim.
  list_str_types <- list(
    "C19_ENC_XTRA_GAJEWSKI" = cols(admit_dispo = "c", discharge_dispo = "c"),
    "C19_RX_ADMIN_GAJEWSKI" = cols(prescript_refills = "c"),
    "C19_RX_ORDER_GAJEWSKI" = cols(prescript_refills = "c")
  )
  print(paste0("Importing ", str_filename))
  columns = cols(mrn = "c", MRN = "c")
  if(str_filename %in% names(list_str_types)){
    columns$cols = c(columns$cols, list_str_types[[str_filename]]$cols)
  }
  tib_import <- read_delim(
      paste0(STR_BIOBANK, STR_BIOBANK_DATAMART, str_filename, ".txt"),
      col_names = TRUE,
      escape_double = TRUE,
      col_types = columns,
      na = c( "", "NA" ),
      delim = "|",
      trim_ws = TRUE
    )
  if("MRN" %in% names(tib_import)) {
    tib_import <- rename(tib_import, mrn = MRN)
  }
  return(
    tib_import
  )
}


```

# Importing inclusion/exclusion criteria and special cohort info
- Long list of specific inclusion/exclusion criteria from separate Excel sheet
- Joining with REDCap list

```{r Annotations}
########################
#  INCLUSION/EXCLUSION #
########################

# Imports manually annotated list of patients by ID and reasons for inclusion/exclusion
# Two columns of "special" annotations and column for tocilizumab use and column for remdesivir use
tib_patients_annotations <- list.files(path = paste0(STR_BIOBANK, STR_BIOBANK_DEMO),
                        pattern = "^Exclusions.*xlsx$",
                        full.names = TRUE) %>%
  magrittr::extract(which.max(file.mtime(.))) %>%
  readxl::read_excel(
    col_names = c("id", "special1", "special2", "tocitext", "rmdstext"), skip = 1
  ) %>%
  unite("specialtext", special1:special2, sep = ", ", na.rm = TRUE) %>%
  mutate(
    # Logical for tocilizumab use
    toci = !is.na(tocitext),
    # Logical for remdesivir use
    rmds = !is.na(rmdstext),
    # Logical for patients with a negative COVID-19 swab
    negative = grepl("neg", specialtext, ignore.case = TRUE),
    # Logical for patients with explicit exclusion criteria
    exclude = grepl("excl", specialtext, ignore.case = TRUE),
    # Logical for patients with marked for special subgroup analyses
    special = grepl("special", specialtext, ignore.case = TRUE),
    # Category of subgroup
    specialcat = case_when(
      special & grepl("[^c]hem", specialtext, ignore.case = TRUE) ~ "Cancer - Hematologic",
      special & grepl("canc", specialtext, ignore.case = TRUE) ~ "Cancer - Solid",
      special & grepl("chemo", specialtext, ignore.case = TRUE) ~ "Cancer - Uncategorized",
      special & grepl("tx", specialtext, ignore.case = TRUE) ~ "Transplant",
      special & grepl("biol.*ab", specialtext, ignore.case = TRUE) ~ "Immunosuppression - Biologics",
      special & grepl("steroid", specialtext, ignore.case = TRUE) ~ "Immunosuppression - Steroids",
      special & grepl("mmf", specialtext, ignore.case = TRUE) ~ "Immunosuppression - Rheumatologic",
      special & grepl("aids", specialtext, ignore.case = TRUE) ~ "Immunosuppression - AIDS"
    ),
    steroids = grepl("Steroids", specialcat),
    # Logical for convalescent plasma donors
    convdonor = grepl("conv.*don", specialtext, ignore.case = TRUE),
    # Logical for convalescent plasma recipients
    convrecip = grepl("conv.*rec", specialtext, ignore.case = TRUE),
    # Logical for patients identified at the curbside transitional clinic
    ctc = grepl("ctc", specialtext, ignore.case = TRUE),
    # Logical for pediatric patients
    peds = grepl("peds", specialtext, ignore.case = TRUE),
    # Logical for patients with lung symptoms
    ili = grepl("ili", specialtext, ignore.case = TRUE),
    # Subgroup with cytosorb or ECMO use
    cytoecmo = grepl("cyto", specialtext, ignore.case = TRUE) | grepl("ecmo", special, ignore.case = TRUE),
    # Defined healthy donors
    healthy = grepl("healthy", specialtext, ignore.case = TRUE),

    # Defining patients to include for flow/cytokine analysis
    basic_include = !negative & !exclude & !special & !peds,

    # Defining patients for healthy controls - not used, only using simple healthy filter above
    # healthy = (negative & !exclude & !special & !peds & !toci) | healthy,

    # Getting convalescent plasma date
    convrecipdate = as.Date(ifelse(
      convrecip,
      as.Date(
        paste0(
          str_extract(
            str_extract(
              specialtext,
              "Conv plasma recipient (- )?[\x28]?\\d+/\\d+"
            ),
            "\\d+/\\d+"
          ),
          "/2020"
        ),
        format = "%m/%d/%Y"
      ),
      NA_Date_
    ))
  ) %>%
  filter(!is.na(id))

########################
#     REDCAP MERGE     #
########################

# List of IDs to with inclusion/exclusion criteria
tib_patients_all <- tib_patients_annotations %>%
  full_join(tib_redcap %>% filter(redcap_repeat_instrument == ""), by = "id") %>%
  mutate(
    across(
      c("toci", "rmds", "negative", "exclude", "special", "convdonor", "convrecip", "ctc", "peds", "ili", "cytoecmo", "healthy"),
      ~replace_na(., FALSE)
    ),
    across(
      c("basic_include"), 
      ~replace_na(., TRUE)
    )
  ) %>%
  filter(!is.na(id)) %>%
  rename(d0 = date_of_covid_symptom_onse) %>%
  mutate(
    d0 = ymd(d0),
    dob_rc = ymd(date_of_birth)
  ) %>%
  unite(symptom_other_detail, other_symptoms, other_symptoms2, sep = ",", na.rm = TRUE, remove = TRUE) %>%
  select(
    id:convrecipdate,
    d0,
    mrn,
    pmh_htn = past_medical_history___1,
    pmh_cad = past_medical_history___2,
    pmh_pad = past_medical_history___3,
    pmh_chf = past_medical_history___4,
    pmh_copd = past_medical_history___5,
    pmh_asthma = past_medical_history___6,
    pmh_phtn = past_medical_history___7,
    pmh_osa = past_medical_history___8,
    pmh_dm = past_medical_history___9,
    pmh_rheum = past_medical_history___10,
    pmh_rheum_details = rheum_diseases,
    pmh_cancer = past_medical_history___11,
    pmh_cancer_details = cancer,
    pmh_other = past_medical_history___12,
    pmh_esrd = past_medical_history___13,
    pmh_dementia = past_medical_history___14,
    symptom_congestion = symptoms_in_hpi___1,
    symptom_rhinorrhea = symptoms_in_hpi___2,
    symptom_cough = symptoms_in_hpi___3,
    symptom_sob = symptoms_in_hpi___4,
    symptom_doe = symptoms_in_hpi___5,
    symptom_headache = symptoms_in_hpi___6,
    symptom_fever = symptoms_in_hpi___7,
    symptom_nv = symptoms_in_hpi___8,
    symptom_diarrhea = symptoms_in_hpi___9,
    symptom_myalgias = symptoms_in_hpi___10,
    symptom_other = symptoms_in_hpi___11,
    symptom_congestion = symptoms_in_hpi___1,
    symptom_other_detail,
    dob_rc,
    death_date
  )

tib_patients_all <- tib_patients_all %>%
  left_join(fun_import_data("C19_PATIENT_DEMO_GAJEWSKI"), by = c("mrn")) %>%
  mutate(
    dob = case_when(
      is.na(birth_date) ~ as.character(dob_rc),
      TRUE ~ as.character(birth_date)
      ) %>% str_remove("\\ ([0-9]|\\:)+"),
    dob = ymd(dob),
    age_d0 = ifelse(
      is.na(d0),
      time_length(difftime(ymd("2020/07/01"), dob), "years"),
      time_length(difftime(d0, dob), "years")
    ),
    death_date = ifelse(
      is.na(death_date.y),
      death_date.x,
      as_date(ymd_hms(death_date.y))
    )
  ) %>%
  select(
    id:symptom_other_detail,
    dob,
    age_d0,
    sex = sex_code,
    religion,
    race,
    ethnic,
    death_date
  )

tib_outpatient_meds <- tib_patients_all %>%
  filter(!is.na(mrn)) %>%
  select(mrn, d0) %>%
  right_join(fun_import_data("C19_RX_OUT_GAJEWSKI")) %>%
  filter(
    (is.na(ORDER_END_TIME) & is.na(END_DATE)) | d0 < ymd_hms(ORDER_END_TIME) | d0 < ymd(END_DATE),
    d0 > ymd_hms(ORDER_START_TIME),
    ORDERING_MODE == "Outpatient"
  ) %>%
  mutate(
    med = sapply(strsplit(as.character(MEDICATION), "[0-9]"), function(x) x[[1]][1]),
    med = sapply(strsplit(as.character(med), "\\("), function(x) x[[1]][1]),
    med = trimws(med)
  ) %>%
  select(mrn, med) %>%
  unique() %>%
  group_by(mrn) %>%
  summarise(
    meds = paste(med, collapse = ","),
    nmeds = n()
  )

tib_patients_all <- tib_patients_all %>%
  left_join(tib_outpatient_meds, by = "mrn")

tib_patients_all <- tib_patients_all %>%
  left_join(
    readxl::read_excel("data/missing_demo.xlsx", sheet = 1) %>%
      mutate(id = as.character(id)),
    by = "id"
  ) %>%
  mutate(
    dob = ifelse(is.na(m_dob), dob, ymd(m_dob)),
    age_d0 = ifelse(is.na(m_dob),
                 ifelse(is.na(m_age), age_d0, m_age),
                 ifelse(
                   is.na(d0),
                   time_length(difftime(ymd("2020/07/01"), m_dob), "years"),
                   time_length(difftime(d0, m_dob), "years")
                 )),
    sex = ifelse(is.na(m_sex), sex, m_sex),
    race = ifelse(is.na(m_race), race, m_race),
    ethnic = ifelse(is.na(m_ethnic), ethnic, m_ethnic)
  )

rm(tib_patients_annotations)
rm(tib_outpatient_meds)
rm(tib_redcap)

########################
#     EXCEL EXPORT     #
########################

# List of all patients in redcap merged with info from above
tib_patients_all %>%
  writexl::write_xlsx(paste0(STR_DATA_DIR_DEMO_CLIN, "patients-fulldemo.xlsx"))

```

# Getting COVID-19 DataMart encounter data
- Creating a list of hospital encounters using billing information and merging in REDCap data on patients to only include the most recent hospital encounter (Inpatient only)

```{r Encounters}
########################
# DATAMART: ENCOUNTERS #
########################

# Creating list of encounters, starting with the "extra" info which includes all the dispo/admit info
tib_encounters_all <- fun_import_data( "C19_ENC_XTRA_GAJEWSKI" ) %>%
  # Only including encounters with a disposition
  filter(!is.na(discharge_dispo_id)) %>%
  # Merging by HAR ID to the primary encounter file by using primary HAR
  left_join(fun_import_data( "C19_ENC_GAJEWSKI" ), by = c("mrn", "har" = "har_primary", "record_type")) %>%
  # Removing outpatient encounters
  filter(encounter_eio == "Inpatient") %>%
  # Removing second HAR column (secondary HARs, already have primary HAR)
  select(-har.y) %>%
  # Grouping by unique MRN/HAR combinations
  group_by(mrn, har, encounter_eio, record_type) %>%
  # Only including pb (hb seems to be more for hospital billing and has month-long ranges)
  filter(record_type == "pb") %>%
  # Removing HARs that correspond to encounters without time data (not useful/clinical)
  filter(!is.na(start_date)) %>%
  summarise(
    mrn,
    har,
    # Getting unique admission/discharge IDs/dispos
    admit_dispo_id = paste(unique(admit_dispo_id[!is.na(admit_dispo_id)]), collapse = ','),
    admit_dispo = paste(unique(admit_dispo[!is.na(admit_dispo)]), collapse = ','),
    discharge_dispo_id = paste(unique(discharge_dispo_id[!is.na(discharge_dispo_id)]), collapse = ','),
    discharge_dispo = paste(unique(discharge_dispo[!is.na(discharge_dispo)]), collapse = ','),
    # Given overlaps in start/end dates for same-HAR encounters during irregular billing codings, taking earliest start and latest end
    start_date = ymd(min(start_date)),
    end_date = ymd(max(end_date)),
    # Merging E/I/O (ED/Inpatient/Outpatient) info by unique
    encounter_eio = paste(unique(encounter_eio[!is.na(encounter_eio)]), collapse = ','),
    # List of unique ICU in/out times
    icu_in_time = paste(unique(icu_in_time[!is.na(icu_in_time)]), collapse = ','),
    icu_out_time = paste(unique(icu_out_time[!is.na(icu_out_time)]), collapse = ',')
  ) %>%
  # Getting unique only
  ungroup() %>%
  unique() %>%
  select(mrn, har, admit_date = start_date, discharge_date = end_date) %>%
  # Joining only patients that are both in REDCap and in DataMart
  inner_join(tib_patients_all %>% select(mrn, d0), by = "mrn")

tib_encounters_include <-  tib_encounters_all %>%
  # Grouping by MRN to limit to 1 encounter per patient as index healthcare episode
  group_by(mrn) %>%
  # Only include encounters that end after day of symptom onset (so includes patients who became symptomatic after hospitalization) and don't start after 30 days
  filter(discharge_date >= d0, admit_date <= d0 + days(30)) %>%
  # Select the first encounter by start date
  slice_min(admit_date) %>%
  select(-d0)

tib_patients_all <- tib_patients_all %>%
  left_join(tib_encounters_include, by = "mrn")

########################
#     EXCEL EXPORT     #
########################

# List of index inpatient encounters per patient (if they exist)
tib_encounters_include %>%
  writexl::write_xlsx(paste0(STR_DATA_DIR_DEMO_CLIN, "encounters-inpatient-index.xlsx"))

rm(tib_encounters_include)

# List of all inpatient encounters per patient (if they exist)
tib_encounters_all %>%
  writexl::write_xlsx(paste0(STR_DATA_DIR_DEMO_CLIN, "encounters-inpatient-all.xlsx"))

rm(tib_encounters_all)
```

# SF Ratio Data
* Anesthesia related FiO2 measures are almost always 90-100 and don't correspond to physiologic need, so currently filtering out

```{r SF Ratio - Data}
########################
#   DATAMART: VITALS   #
########################

# Getting all oxygenation measurements directly from DataMart
tib_meas_vitals_all <- tib_patients_all %>%
  select(id, mrn, har, discharge_date) %>%
  left_join(fun_import_data( "C19_FLOW_GAJEWSKI" ), by = "mrn") %>%
  mutate(meas_time = ymd_hms(recorded_time),
         meas_date = as_date(meas_time)) %>%
  filter(meas_date <= discharge_date) %>%
  select(id, meas_name = flo_meas_name, meas_time, value = meas_value, group = flo_group_name)

## Getting reference measurement names
# Getting device information
tib_meas_o2device <- tib_meas_vitals_all %>%
  filter(grepl("oxygen device|o2 deliv", group, ignore.case = TRUE)) %>%
  rename(device = value) %>% select(-meas_name) %>%
  mutate(
    device_group = factor(
      case_when(
        device == "Room Air" ~ "1",
        grepl("vent", device, ignore.case = TRUE) ~ "4",
        grepl("bipap|cpap|high flow", device, ignore.case = TRUE) ~ "3",
        TRUE ~ "2"
      ),
      levels = c("1","2","3","4")
    )
  )
# Getting FIO2 levels
# - Ignoring all anesthesia measurements given likelihood of near 100% FiO2 without a physiologic need/pathologic correlate 
# - Removing ECMO blender values because this is always going to be at 100% and is used for the circuit
tib_meas_fio2 <- tib_meas_vitals_all %>%
  filter(grepl("fio2", group, ignore.case = TRUE), !grepl("anes|ecmo", meas_name, ignore.case = TRUE)) %>%
  mutate(value = as.double(gsub("[^0-9.]", "", value))) %>%
  filter(!is.na(value), value <= 100, value >= 21) %>%
  rename(fio2 = value, fio2meas = meas_name)
# Getting all pulse ox measurements
tib_meas_spo2 <- tib_meas_vitals_all %>%
  filter(grepl("spo2", group, ignore.case = TRUE)) %>%
  mutate(value = as.double(gsub("[^0-9.]", "", value))) %>%
  filter(!is.na(value), value <= 100, value >= 0) %>%
  filter(!grepl("PEWS", meas_name)) %>%
  rename(spo2 = value) %>% select(-meas_name)
# Getting liters/minute flow
tib_meas_liters <- tib_meas_vitals_all %>%
  filter(grepl("oxygen flow", group, ignore.case = TRUE)) %>%
  mutate(value = as.double(gsub("[^0-9.]", "", value))) %>%
  filter(!is.na(value), value <= 15, value >= 0) %>%
  rename(liters = value) %>% select(-meas_name)

########################
#       SF RATIO       #
########################

# Merging all measurements
tib_sfratio_devices <- tib_meas_spo2 %>%
  full_join(tib_meas_fio2, by = c("id", "meas_time")) %>%
  full_join(tib_meas_liters, by = c("id", "meas_time")) %>%
  full_join(tib_meas_o2device, by = c("id", "meas_time")) %>%
  group_by(id) %>%
  arrange(id, meas_time) %>%
  # Only use information from liters/minute when there is no FiO2 already specified, as these are likely from HFNC
  mutate(
    liters = case_when(
      !is.na(fio2) ~ 0,
      TRUE ~ liters
    ),
    device_group = replace(device_group, row_number() == 1, "1"),
    device_group = factor(
        case_when(
        !is.na(liters) & liters > 0 & liters < 7 ~ "2",
        !is.na(liters) & liters == 0 & fio2 == 21 ~ "1",
        TRUE ~ as.character(device_group)
      ),
      levels = c("1","2","3","4")
    )
  ) %>%
  # Given not all SpO2 measurements are accompanied by a change in LPM, propagate all values down the column
  fill(device_group, liters) %>%
  complete(device_group, fill = list("1")) %>%
  # Generate an FiO2 when LPM exist and no FiO2 exists or for room air
  mutate(fio2 = case_when(
    is.na(fio2) & !is.na(liters) & liters > 0 ~ 20 + liters*4,
    is.na(fio2) & (device_group == "1" | is.na(device_group)) ~ 21,
    TRUE ~ fio2
    )
  ) %>%
  # Filling in all FiO2 values
  fill(fio2) %>%
  # Filling in all the device types
  fill(device_group) %>%
  # Remove rows with no SpO2 measurement
  filter(!is.na(spo2)) %>%
  # Calculate the SF ratio (SpO2/FiO2 - x100 for ratio)
  mutate(sfratio = spo2/fio2*100.0) %>%
  # Getting patient data
  full_join(tib_patients_all, by = c("id")) %>%
  # Calculating time since symptom onset
  filter(meas_time > as_datetime(d0)) %>%
  mutate(date = as_date(meas_time),
         day = as.integer(date - d0)) %>%
  filter(
    # Exclude values for patients who transitioned to CMO
    !((id == "207") & (meas_time >= as.POSIXct("2020-05-05 13:00:00",format="%Y-%m-%d %H:%M:%OS",tz="Etc/GMT-5"))),
    !((id == "211") & (meas_time >= as.POSIXct("2020-06-26 21:48:00",format="%Y-%m-%d %H:%M:%OS",tz="Etc/GMT-5"))),
    !((id == "566") & (meas_time >= as.POSIXct("2020-09-09 15:40:00",format="%Y-%m-%d %H:%M:%OS",tz="Etc/GMT-5"))),
    # Excluding very obvious human entry error
    spo2 != 9
  ) %>%
  ungroup() %>%
  group_by(id) %>%
  filter(min(day) <= 30) %>%
  ungroup() %>%
  select(id, sfratio, day, date, device_group, fio2, spo2) %>%
  # Adding in patients who did not have a hospitalization (assumed low severity)
  full_join(tib_patients_all %>% filter(!healthy) %>% select(id), by = "id") %>%
  mutate(sfratio = ifelse(is.na(sfratio), 100.0/0.21, sfratio)) %>%
  ungroup()

tib_sfratio_all <- tib_sfratio_devices %>% group_by(id, date, day) %>%
  summarise(
    sfratio_mean = mean(sfratio)
  ) %>%
  ungroup() %>%
  group_by(id) %>%
  mutate(
    sfseverity_highest = cut(min(sfratio_mean), breaks = SF_BREAKS, labels = sflevels(), right = FALSE),
    sfratio_lowest = min(sfratio_mean)
  ) %>%
  mutate(admission_length = max(day) - min(day)) %>%
  ungroup()

tib_patients_all <- tib_patients_all %>%
  left_join(
    tib_sfratio_all %>%
      select(-day, -date, -sfratio_mean) %>%
      unique()
  ) %>%
  mutate(
    sfseverity_highest = factor(
      ifelse(
        healthy,
        "Healthy",
        as.character(sfseverity_highest)
      ),
      levels = sflevels(TRUE)
    )
  )

tib_sfratio_all <- tib_sfratio_all %>%
  select(-sfseverity_highest, -sfratio_lowest, -admission_length) %>%
  filter(!is.na(day))

tib_patients_all <- tib_patients_all %>%
  left_join(
    tib_sfratio_all %>%
      group_by(id) %>%
      summarise(
        severe_days = sum(sfratio_mean < SF_BREAKS[2]),
        moderate_days = sum(sfratio_mean < SF_BREAKS[3])) %>%
      mutate(moderate_severe_days = moderate_days + severe_days),
    by = "id"
  )

tib_sfratio_all %>% writexl::write_xlsx("../../help.xlsx")
rm(tib_meas_fio2)
rm(tib_meas_spo2)
rm(tib_meas_liters)
rm(tib_meas_o2device)

```

# Cytokine data
* Using Python again to generate luminex data as a CSV file, able to take in multiple formats of Excel files due to operator dependencies

```{r Cytokine - Data}
########################
#   LUMINEX RAW DATA   #
#       -PYTHON-       #
########################

# Luminex runs
#list_plex <- list("44", "30", "6")
list_plex <- list("30", "6")

# Processing Luminex output and manual Excel annotations into CSV files
lapply(list_plex, function(plex) {py_run_file(paste0(STR_CODE_DIR_CYTOKINE, "luminex2CSV_", plex, "plex.py"))})

########################
#    LUMINEX IMPORT    #
########################

# Importing each processed Luminex file
fun_import_luminex <- function(plex) {
  tib_cyto_names <- readxl::read_excel(paste0(STR_DATA_DIR_CYTOKINE,"cytokine_names.xlsx"))
  tib_cyto_drop <- tib_cyto_names %>% filter(is.na(name)) %>% select(Plex44)
  list_tib_cyto_names <- list(
    "6" = select(filter(tib_cyto_names, !is.na(Plex6)), Plex6, name),
    "30" = select(filter(tib_cyto_names, !is.na(Plex30)), Plex30, name)
  #  "44" = select(filter(tib_cyto_names, !is.na(Plex44)), Plex44, name)
  )
  tib_cytokines <- list.files(path = STR_DATA_DIR_CYTOKINE,
             pattern = paste0("lum.*", plex, "plex.csv$"),
             full.names = TRUE) %>%
    magrittr::extract(which.max(file.mtime(.))) %>%
    read_csv(col_types = cols(.default = "c")) %>%
    mutate(id = as.character(id), date = date(date), sample = Sample) %>%
    group_by(id, date, sample, bmp_sample) %>%
    mutate(
      dup = n(),
      bmp_sample = str_replace(str_replace(bmp_sample, "^b\\'", ""), "\\'$", ""),
      bmp_sample = ifelse(grepl("Normal", bmp_sample), NA_character_, bmp_sample),
      bmp = grepl("bmp", bmp_sample, ignore.case = "") | grepl("^[A-Z][0-9]+", bmp_sample),
      id = case_when(
        grepl("Normal", id) ~ "515",
        id == "175" ~ "176",
        TRUE ~ id
      )
    ) %>%
    select(
      -Location,
      -Sample
    )
  if(plex == "44") {
    for(cyto in tib_cyto_drop){
      tib_cytokines <- tib_cytokines %>% select(-contains(cyto))
    }
  }
  for(i in 1:length(list_tib_cyto_names[[plex]]$name)) {
    tib_cytokines <- tib_cytokines %>% rename_with(
      ~gsub(list_tib_cyto_names[[plex]][[paste0("Plex",plex)]][i], list_tib_cyto_names[[plex]][["name"]][i], .x, fixed = TRUE))
  }
  return(tib_cytokines)
}

# Mark duplicates
fun_cytokines_dups_plex <- function(tib_plex) {
  tib_dups <- tib_plex %>%
    filter(dup > 1) %>%
    arrange(.by_group = TRUE) %>%
    select(-starts_with("LIMIT")) %>%
    summarise(across(ends_with("result"), ~ (max(as.double(.x)) - min(as.double(.x)))/mean(as.double(.x))*100))
  return(tib_dups)
}

# Merge all duplicates together
fun_cytokines_dups_all <- function(list_tib_cytokines) {
  all_plex_samples <- Reduce(function(x,y){full_join(x, y, by = c("id", "date"))}, list_tib_cytokines) %>%
    select(id, date) %>%
    unique()
  tib_cytokines_dups_all <- fun_cytokines_dups_plex(bind_rows(lapply(list_tib_cytokines, right_join, all_plex_samples)))
  return(tib_cytokines_dups_all)
}

list_tib_cytokines <- lapply(list_plex, fun_import_luminex)
rm(list_plex)
list_tib_cytokines_dups <- lapply(list_tib_cytokines, fun_cytokines_dups_plex)
tib_cytokines_dups_all <- fun_cytokines_dups_all(list_tib_cytokines)
rm(list_tib_cytokines_dups)

purchased_donors <- list("ND05", "ND378", "ND426", "ND439", "ND476", "ND479")

# Importing Luminex data, binning into day groups after calculating days after symptom onset
tib_cytokine_all <- bind_rows(list_tib_cytokines) %>%
  mutate(id = as.character(id),
         id = ifelse(id %in% purchased_donors, id, str_remove(str_remove(id, "ND0"), "ND")),
         date = ymd(date)) %>%
  left_join(tib_patients_all %>% select(id, d0, healthy), by = "id") %>%
  mutate(
    date = as_date(ifelse(healthy, NA_Date_, date)),
    day = as.integer(ifelse(is.na(date), NA_real_, date - d0))
  )

rm(list_tib_cytokines)
rm(purchased_donors)

# Get list of all cytokine names/measures
cytokine_names <- tib_cytokine_all %>%
  ungroup() %>%
  select(starts_with("LIMIT")) %>%
  colnames() %>%
  str_replace("LIMIT", "")

tib_cytokine_all <- tib_cytokine_all %>% type_convert() %>% ungroup()

# Boolean for whether to extrapolate additional values or not
extrapolate <- TRUE

# For loop in order to change values in place
for(cytokine in cytokine_names) {
  cytokine_lim <- paste0("LIMIT", cytokine)
  # Get values at which a "<" was present in original raw data
  cytokine_min_measure <- tib_cytokine_all %>%
    ungroup() %>%
    filter(as.character(!!sym(cytokine_lim)) == "MIN") %>%
    select(cytokine) %>%
    unique() %>% unlist() %>% as.double()
  if(!length(cytokine_min_measure)) {cytokine_min_measure = 0}
  # Get values at which a ">" was present in original raw data
  cytokine_max_measure <- tib_cytokine_all %>%
    ungroup() %>%
    filter(as.character(!!sym(cytokine_lim)) == "MAX") %>%
    select(str_replace(cytokine, "LIMIT", "")) %>%
    unique() %>% unlist() %>% as.double()
  if(!length(cytokine_max_measure)) {cytokine_max_measure = Inf}
  # Get lowest extrapolated value
  cytokine_min_extrap <- tib_cytokine_all %>%
    ungroup() %>%
    pull(cytokine) %>%
    min(na.rm = TRUE) %>% unlist()
  # Get highest extrapolated value
  cytokine_max_extrap <- tib_cytokine_all %>%
    ungroup() %>%
    pull(cytokine) %>%
    max(na.rm = TRUE) %>% unlist()
  # Mark extrapolated values as MIN_EXTRAP or MAX_EXTRAP
  tib_cytokine_all[[cytokine_lim]] = case_when(
    tib_cytokine_all[[cytokine]] < cytokine_min_measure ~ "MIN_EXTRAP",
    tib_cytokine_all[[cytokine]] > cytokine_max_measure ~ "MAX_EXTRAP",
    TRUE ~ as.character(tib_cytokine_all[[cytokine_lim]])
  )
  tib_cytokine_all[[cytokine]] <- case_when(
    # If extrapolate boolean is TRUE, use min/max extrapolated values
    (extrapolate & (tib_cytokine_all[[cytokine_lim]] == "MIN")) ~ cytokine_min_extrap,
    (extrapolate & (tib_cytokine_all[[cytokine_lim]] == "MAX")) ~ cytokine_max_extrap,
    # Otherwise, set all values that were extrapolated to the lower/upper limits of non-extrapolated measure
    (!extrapolate & (tib_cytokine_all[[cytokine]] < cytokine_min_measure)) ~ cytokine_min_measure,
    (!extrapolate & (tib_cytokine_all[[cytokine]] > cytokine_max_measure)) ~ cytokine_max_measure,
    TRUE ~ tib_cytokine_all[[cytokine]]
  )
}

# Removing "LIMIT" columns
tib_cytokine_all <- tib_cytokine_all %>%
  ungroup() %>%
  select(-starts_with("LIMIT"))

list_cytokines_all <- str_replace(colnames(select(tib_cytokine_all, ends_with("result"))), "_result", "")

for (cytokine in list_cytokines_all) {
  tib_cytokine_all <- tib_cytokine_all %>%
  rename(
    result = paste(cytokine,"result", sep = "_"),
    count = paste(cytokine,"count", sep = "_"),
    cv = paste(cytokine,"cv-replicates", sep = "_"),
  ) %>%
  # Remove N/A value results
  mutate(
    result = case_when(
      is.na(count) | is.na(cv) ~ NA_real_,
      (count > 32) & (cv < 20) ~ result,
      TRUE ~ NA_real_
    )
  ) %>%
  rename(
    !!cytokine := result
  ) %>%
  select(
    -count,
    -cv
  )
}

tib_cytokine_all <- tib_cytokine_all %>%
  mutate(
    bmp_sample = str_replace(str_replace(bmp_sample, "^b\\'", ""), "\\'$", ""),
    bmp = grepl("bmp", bmp_sample, ignore.case = "") | grepl("^[A-Z][0-9]+", bmp_sample)
  ) %>%
  group_by(id, date, day, healthy, bmp, bmp_sample, luminex_day) %>%
  summarise(across(all_of(list_cytokines_all), ~mean(.x, na.rm = TRUE)*2)) %>%
  filter_at(list_cytokines_all, any_vars(!is.na(.)))

# All cytokine data
tib_cytokine_all %>%
  writexl::write_xlsx(paste0(STR_DATA_DIR_CYTOKINE, "cytokine_all.xlsx"))

tib_cytokine_all <- tib_cytokine_all %>%
  ungroup() %>%
  filter(!bmp | healthy) %>%
  group_by(id, date, day) %>%
  summarise(across(all_of(list_cytokines_all), ~mean(.x, na.rm = TRUE))) %>%
  ungroup() %>%
  group_by(id, date, day) %>%
  mutate(
    across(everything(), ~ifelse(is.nan(.x), NA_real_, .x))
  ) %>%
  ungroup()

# QC: Duplicates marked and grouped
tib_cytokines_dups_all %>%
  writexl::write_xlsx(paste0(STR_DATA_DIR_CYTOKINE, "cytokine_duplicates.xlsx"))
rm(tib_cytokines_dups_all)

```

# Lab Data
* Getting lab data

```{r Lab - Data}
########################
#    DATAMART: LABS    #
########################

# Importing DataMart for labs
tib_labs_all <- fun_import_data( "C19_LABS_GAJEWSKI" ) %>%
  select(
    mrn,
    time = spec_take_time,
    lab = component_name,
    value = ord_value
  ) %>%
  inner_join(tib_patients_all %>% filter(!is.na(d0)) %>% select(mrn, id, d0), by = c("mrn")) %>%
  left_join(tib_columns %>% select(variable, name), by = c("lab" = "variable")) %>%
  # Calculating time since symptom onset
  filter(ymd_hms(time) - as_datetime(d0) >= 0) %>%
  mutate(dt = ymd_hms(time),
         date = as_date(dt),
         day = as.integer(date - d0)) %>%
  filter(!grepl("unable|could not|rejected|received|duplicate|resubmit|incorrect|unsatisf|too old|hemolyzed|sample clotted|cancel|grossly lipemic|not performed|cannot calculate|error|invalid|incorrect|not suff|please contact|therefore|DR.|corrected|request|at [0-9]+ on|at [0-9]+ by|see note|please see|critical value|infection control|removal resin|[0-9][0-9]\\:[0-9][0-9]|[0-9]+\\/[0-9]+\\/[0-9]+|notification|refer to|require isolation|incalc|not measured", value, ignore.case = TRUE)) %>%
  mutate(value = as.numeric(str_remove(value, ">")),
         id = as.character(id)) %>%
  filter(!is.nan(value) & !is.na(value)) %>%
  group_by(id, name, day, date) %>%
  filter(!is.na(name)) %>%
  arrange(dt) %>%
  slice_head(n=1) %>%
  ungroup() %>%
  select(-time, -dt, -lab, -mrn, -d0) %>%
  spread(name, value) %>%
  ungroup()

```

# Medication Data
* Getting medication data

```{r Medication - Data}
########################
#    DATAMART: MEDS    #
########################

meds_of_interest <- "lopinavir|azithromycin|hydroxychloroquine|tocilizumab|remdesivir|dexathasone|prednisone"

# Importing DataMart for labs
tib_meds_patient <- fun_import_data( "C19_RX_ADMIN_GAJEWSKI" ) %>%
  filter(
    grepl(meds_of_interest, medication_name, ignore.case = TRUE)
  ) %>%
  inner_join(
    tib_patients_all %>% filter(!is.na(har)) %>% select(id, mrn, har),
    by = c("mrn", "har")
  ) %>%
  filter(
    !is.na(take_med_dttm)
  ) %>%
  separate(
    medication_name,
    c("medication"),
    sep = " ",
    extra = "drop"
  ) %>%
  select(id, medication) %>% # , toci, rmds
  unique() %>%
  group_by(id) %>% #, toci, rmds
  summarise(inpt_medications=paste(medication, collapse=","))

tib_patients_all <- tib_patients_all %>%
  left_join(tib_meds_patient, by = "id") %>%
  mutate(
    Tocilizumab = grepl("tocilizumab", inpt_medications, ignore.case = TRUE),
    Remdesivir = grepl("remdesivir", inpt_medications, ignore.case = TRUE),
    `Lopinavir/Ritonavir` = grepl("lopinavir", inpt_medications, ignore.case = TRUE),
    Azithromycin = grepl("azithromycin", inpt_medications, ignore.case = TRUE),
    Hydroxychloroquine = grepl("hydroxychloroquine", inpt_medications, ignore.case = TRUE),
    Steroid = grepl("dexamethasone|prednisone", inpt_medications, ignore.case = TRUE)
  )

rm(meds_of_interest)
rm(tib_meds_patient)
```

# Flow Cytometry
* Getting flow data from PBMCs

```{r Flow - Data}

########################
#     FLOW SAMPLES     #
########################

# Importing flow sample info
tib_flow_samples <- list.files(path = paste0(STR_BIOBANK, "Flow/Data/results"),
                        pattern = "^sample.*xlsx$",
                        full.names = TRUE) %>%
  magrittr::extract(which.max(file.mtime(.))) %>%
  readxl::read_excel(
    col_names = c("flowid", "id", "date", "exp", "qc", "sample", "flowmatch", "unique"), 
    col_types = c("text", "text", "date", "skip", "text", "text", "text", "text"), 
    skip = 1
  )


########################
#      FLOW DATA       #
########################

# Getting flow raw data, first getting each of the individual text file names
list_flow_files <- as.list(unlist(list(
  3:10,
  "11-12"
)))

tib_flow_raw <- lapply(
    list_flow_files,
    function(exp) {
      return(
        list.files(path = paste0(STR_BIOBANK, "Flow/Data/results"),
               pattern = paste0("^Exp", exp, ".*txt$"),
               full.names = TRUE)[1]
      )
    }
  ) %>%
  # Importing each TSV, forcing the type of each column as a character
  lapply(
    read_tsv,
    col_types = cols(.default = "c")
  ) %>%
  # Adding experiment numbers to each sample name to be able to merge
  # with sample info
  map2(
    list_flow_files,
    function(tib, exp) {
      return(
        mutate(
          tib,
          flowmatch = paste0(`Sample:`, "_Exp", exp)
        )
      )
    }
  ) %>%
  # Merging each tibble together by row
  bind_rows() %>%
  # Removing sample column
  select(-`Sample:`) %>%
  # Removing means/SDs from each experiment
  filter(
    !grepl("Mean_", flowmatch),
    !grepl("SD_", flowmatch)
  )

# Merging sample info with flow data
tib_flow_all <- tib_flow_samples %>%
  left_join(
    tib_flow_raw,
    by = c("flowmatch")
  ) %>%
  filter(
    !grepl("FSH", flowid)
  ) %>%
  # QC: Removing contaminated samples
  filter(qc != "contaminated") %>%
  select(-flowid, -qc, -sample, -flowmatch, -unique)

# Renaming flow samples
list_skip <- colnames(tib_flow_all %>% select(id:date))
fun_flowname <- function(flow) {
  if(flow %in% list_skip) return(flow)
  return(tail(str_split(flow, "/")[[1]], n = 1))
}
# Renaming flow samples
colnames(tib_flow_all) <- unlist(lapply(colnames(tib_flow_all), fun_flowname))
list_flow_names <- colnames(tib_flow_all %>% select(-(id:date)))

tib_flow_all <- tib_flow_all %>%
  mutate(across(all_of(list_flow_names), ~as.numeric(.))) %>%
  inner_join(tib_patients_all %>% select(id, d0, healthy), by = c("id")) %>%
  mutate(date = ymd(case_when(healthy ~ "", TRUE ~ as.character(date))),
         day = as.integer(date - d0)) %>%
  relocate(id, date, day) %>%
  select(-healthy, -d0) %>%
  group_by(id, date, day) %>%
  summarise(across(all_of(list_flow_names), ~mean(.x, na.rm = TRUE))) %>%
  ungroup()

rm(list_flow_files)
rm(tib_flow_samples)
rm(tib_flow_raw)

```

# ELISA

```{r ELISA - Data}
########################
#    ELISA SAMPLES     #
########################

str_elisa <- list.files(path = paste0(STR_BIOBANK, "ELISA"),
                        pattern = "^A.*xlsx$",
                        full.names = TRUE) %>%
  magrittr::extract(which.max(file.mtime(.)))

# Importing ELISA data
tib_elisa_raw <- bind_rows(
    readxl::read_excel(str_elisa,
        col_names = c("id", "date", "value", "ig"), 
        col_types = c("text", "date", "numeric", "text", "skip", "skip", "skip", "skip", "skip", "skip", "skip"), 
        skip = 1,
        sheet = 1
      ) %>%
      mutate(sr = "Spike"),
    readxl::read_excel(str_elisa,
        col_names = c("id", "date", "value", "ig"), 
        col_types = c("text", "date", "numeric", "text", "skip", "skip", "skip", "skip", "skip", "skip", "skip"), 
        skip = 1,
        sheet = 2
      ) %>%
      mutate(sr = "RBD")
  ) %>%
  inner_join(tib_patients_all %>% select(id, d0, healthy)) %>%
  mutate(
    ig = factor(ig),
    sr = factor(sr),
    date = ymd(case_when(healthy ~ "", TRUE ~ as.character(date))),
    day = as.integer(date - d0)
  ) %>%
  select(-healthy)
               
tib_elisa_all <- tib_elisa_raw %>%
  select(-d0) %>%
  unite(column, c(ig, sr), sep = " ") %>%
  group_by(id, date, day, column) %>%
  summarise(value = mean(value, na.rm = TRUE)) %>%
  spread(column, value) %>%
  ungroup()
```

# Viral

```{r Viral - Data}
# Viral limit of detection
tib_viral_all <- list.files(path = paste0(STR_BIOBANK, "ddPCR"),
                        pattern = "^d.*xlsx$",
                        full.names = TRUE) %>%
  magrittr::extract(which.max(file.mtime(.))) %>%
  readxl::read_excel(
    col_names = c("id", "ddpcr_instrument", "date", "ddpcr_n1", "ddpcr_n2", "ddpcr_r"), 
    col_types = c("text", "text", "skip", "date", "skip", "skip", "skip", "numeric", "numeric", "numeric", "skip"), 
    skip = 1,
    sheet = 10
  ) %>%
  mutate(
    id = case_when(
      id == "547" ~ "540",
      TRUE ~ id
    )
  ) %>%
  left_join(tib_patients_all %>% select(id, d0, healthy), by = "id") %>%
  mutate(
    date = ymd(case_when(healthy ~ "", TRUE ~ as.character(date))),
    day = as.integer(date - d0)
  ) %>%
  mutate(
    ddpcr_n = (ddpcr_n1 + ddpcr_n2)/2.0
  ) %>%
  select(id, date, day, ddpcr_n)

tib_viral_all %>% filter(ddpcr_n > 10^5) %>% select(id, ddpcr_n) %>%
  writexl::write_xlsx(paste0(STR_DATA_DIR_OTHER, "high_viral_loads.xlsx"))

```

# Elispot

```{r Elispot - Data}
tib_elispot_all <- list.files(path = paste0(STR_BIOBANK, "ELISPOT/Final data"),
                        pattern = "^E.*_R.xlsx$",
                        full.names = TRUE) %>%
  magrittr::extract(which.max(file.mtime(.))) %>%
  readxl::read_excel(
    col_names = c("qc", "id", "date", "elispot_pma", "elispot_irrel_pep", "elispot_mhc_ii_control", "elispot_mhc_i_control", "elispot_s_pep", "elispot_m_pep", "elispot_n_pep", "elispot_s_m_n"),
    col_types = c("text", "text", "date", "numeric", "text", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "skip", "skip", "skip"),
    skip = 1,
    sheet = 1
  ) %>%
  mutate(
    elispot_irrel_pep = as.numeric(ifelse(grepl("NaN",elispot_irrel_pep), NA_character_,elispot_irrel_pep)),
    qc = !grepl("Fail", qc)
  ) %>%
  filter(
    qc
  ) %>%
  left_join(tib_patients_all %>% select(id, d0, healthy), by = "id") %>%
  mutate(
    date = ymd(case_when(healthy ~ "", TRUE ~ as.character(date))),
    day = as.integer(date - d0)
  ) %>%
  filter(
    !(id == 584 & date > ymd("2020-06-25")),
    !(id == 576 & date > ymd("2020-06-25")),
    !(id == 618)
  ) %>%
  select(id, date, day, elispot_s_m_n) %>%
  group_by(id, date, day) %>%
  summarise(elispot_s_m_n = mean(elispot_s_m_n)) %>%
  ungroup()

```

# Vitals

```{r Vitals - Data}
list_id <- c("id", "date", "day")

# Getting all vitals measures
tib_meas_vitals_use <- tib_meas_vitals_all %>%
  filter(grepl("bp|height|weight|pulse|temp", group, ignore.case = TRUE) | grepl("respirations|glasgow", meas_name, ignore.case = TRUE)) %>%
  left_join(tib_patients_all %>% select(id, d0, healthy), by = c("id")) %>%
  filter(ymd_hms(meas_time) > as_datetime(d0), !healthy) %>%
  # Calculating time since symptom onset
  mutate(date = as_date(meas_time),
         day = as.integer(date - d0)) %>%
  group_by(id, meas_name, day) %>%
  arrange(meas_time)

# Summarizing vitals, with BP, height/weight/BMI, pulse, temp, resp, and GCS
tib_vitals_all <- tib_meas_vitals_use %>%
  ungroup() %>%
  select(id, date, day) %>%
  unique() %>%
  # Blood Pressure
  left_join(
    tib_meas_vitals_use %>%
      filter(grepl("bp", group, ignore.case = TRUE)) %>%
      separate(value, c("SBP", "DBP"), sep = "\\/") %>%
      mutate(
        SBP = as.numeric(SBP),
        DBP = as.numeric(DBP),
        MAP = as.numeric(SBP)/3.0 + as.numeric(DBP)*2.0/3.0
      ) %>%
      filter(SBP > 0 & DBP > 0) %>%
      group_by(id, date, day) %>%
      arrange(MAP) %>%
      summarise(
        DBP = mean(DBP),
        SBP = mean(SBP)
      ),
    by = unlist(list_id)
  ) %>%
  # Height/Weight/BMI
  left_join(
    full_join(
      tib_meas_vitals_use %>%
        filter(grepl("height", group, ignore.case = TRUE)) %>%
        mutate(
          vitals_height_cm  = as.numeric(value)*2.54
        ) %>%
        ungroup() %>%
        group_by(id) %>%
        arrange(meas_time) %>%
        summarise(
          vitals_height_cm_admit = head(vitals_height_cm, n = 1)
        ),
      tib_meas_vitals_use %>%
        filter(grepl("weight", group, ignore.case = TRUE)) %>%
        mutate(
          vitals_weight_kg  = as.numeric(value)/35.27396194958
        ) %>%
        ungroup() %>%
        group_by(id, date, day) %>%
        arrange(meas_time) %>%
        summarise(
          vitals_weight_kg_admit = head(vitals_weight_kg, n = 1)
        ),
      by = "id"
    ) %>%
    mutate(BMI = vitals_weight_kg_admit/(vitals_height_cm_admit*vitals_height_cm_admit*0.0001)),
    by = unlist(list_id)
  ) %>%
  # Pulse
  left_join(
    tib_meas_vitals_use %>%
      filter(grepl("pulse", group, ignore.case = TRUE)) %>%
      mutate(
        vitals_pulse = as.numeric(value)
      ) %>%
      filter(vitals_pulse > 0) %>%
      group_by(id, date, day) %>%
      arrange(vitals_pulse) %>%
      summarise(
        Pulse = mean(vitals_pulse)
      ),
    by = unlist(list_id)
  ) %>%
  left_join(
    tib_meas_vitals_use %>%
      filter(grepl("temp", group, ignore.case = TRUE)) %>%
      mutate(
        vitals_temp_f = as.numeric(value)
      ) %>%
      filter(vitals_temp_f > 0) %>%
      group_by(id, date, day) %>%
      arrange(vitals_temp_f) %>%
      summarise(
        Temp = tail(vitals_temp_f, n = 1)
      ),
    by = unlist(list_id)
  ) %>%
  # Respirations
  left_join(
    tib_meas_vitals_use %>%
      filter(grepl("respirations", meas_name, ignore.case = TRUE)) %>%
      mutate(
        vitals_resp = as.numeric(value)
      ) %>%
      filter(vitals_resp > 0) %>%
      group_by(id, date, day) %>%
      arrange(vitals_resp) %>%
      summarise(
        `Respiratory Rate` = mean(vitals_resp)
      ),
    by = unlist(list_id)
  ) %>%
  ungroup() %>%
  group_by(id) %>%
  select(
    id, date, day,
    SBP, DBP, Pulse, `Respiratory Rate`, BMI, Temp
  )


```

# Vitamin D

```{r Vitamin D - Data}
tib_vitd_all <- list.files(path = paste0(STR_BIOBANK, "Vit D"),
                        pattern = "^.*.xls$",
                        full.names = TRUE) %>%
  magrittr::extract(which.max(file.mtime(.))) %>%
  readxl::read_excel(
    col_names = c("id", "Vitamin D2", "Vitamin D3"),
    col_types = c("text", "skip", "skip", "skip", "skip", "skip", "skip", "skip", "skip", "skip", "text", "text"),
    skip = 9,
    sheet = 1
  ) %>%
  separate(
    id,
    c("batch", "id", "date", "source"),
    sep = "-"
  ) %>%
  mutate(
    `Vitamin D2` = as.double(str_remove_all(`Vitamin D2`, "<")),
    `Vitamin D3` = as.double(str_remove_all(`Vitamin D3`, "<")),
    date = mdy(date),
    id = ifelse(id == "TC966", "CTC966", id)
  ) %>%
  select(-batch, -source) %>%
  left_join(
    list.files(path = paste0(STR_BIOBANK, "Demographics, controls, ect"),
                        pattern = "^CTC.xl.*$",
                        full.names = TRUE) %>%
      magrittr::extract(which.max(file.mtime(.))) %>%
      readxl::read_excel(
        col_names = c("realid", "ctc1", "ctc2"),
        col_types = c("text", "skip", "skip", "skip", "skip", "text", "text"),
        skip = 1,
        sheet = 1
      ) %>%
      filter(!is.na(ctc1)) %>%
      pivot_longer(cols = starts_with("ctc"), names_to = "ctcn", names_prefix = "", values_to = "ctc", values_drop_na = TRUE) %>%
      mutate(ctc = paste0("CTC", ctc)) %>% select(-ctcn),
    by = c("id" = "ctc")
  ) %>%
  mutate(
    id = ifelse(is.na(realid), id, realid)
#    id = ifelse(id == "CTC950", "470", id)
  ) %>%
  select(-realid) %>%
  left_join(tib_patients_all %>% select(id, d0), by = "id") %>%
  mutate(day = as.integer(date - d0),
         date = as_date(ifelse(is.na(d0), NA, date))) %>% select(-d0)
  
  

```

# ANC/ALC and Flow

```{r ANC and ALC}

list_absolute_counts <- c("AEC", "AMC", "ANC", "ALC")

tib_absolute <- tib_labs_all %>%
  select(id, date, day,
         AEC = `Absolute eosinophils`,
         AMC = `Absolute Monocytes`,
         ANC = `Absolute neutrophils`,
         ALC = `Absolute lymphocytes`) %>%
  filter(across(all_of(list_absolute_counts), ~(!is.na(.))))

tib_absolute_expanded <- tib_absolute %>%
  full_join(tib_absolute %>%
    select(id, date, day, AEC_after = AEC, AMC_after = AMC, ANC_after = ANC, ALC_after = ALC) %>%
    mutate(date = date - days(1), day = day - 1),
    by = c("id", "date", "day")) %>%
  full_join(tib_absolute %>%
    select(id, date, day, AEC_before = AEC, AMC_before = AMC, ANC_before = ANC, ALC_before = ALC) %>%
    mutate(date = date + days(1), day = day + 1),
    by = c("id", "date", "day")) %>%
  mutate(
    AEC = case_when(!is.na(AEC) ~ AEC,
                    !is.na(AEC_before) & !is.na(AEC_after) ~ (AEC_before + AEC_after)/2,
                    !is.na(AEC_before) ~ AEC_before,
                    TRUE ~ AEC_after),
    AMC = case_when(!is.na(AMC) ~ AMC,
                    !is.na(AMC_before) & !is.na(AMC_after) ~ (AMC_before + AMC_after)/2,
                    !is.na(AMC_before) ~ AMC_before,
                    TRUE ~ AMC_after),
    ANC = case_when(!is.na(ANC) ~ ANC,
                    !is.na(ANC_before) & !is.na(ANC_after) ~ (ANC_before + ANC_after)/2,
                    !is.na(ANC_before) ~ ANC_before,
                    TRUE ~ ANC_after),
    ALC = case_when(!is.na(ALC) ~ AEC,
                    !is.na(ALC_before) & !is.na(ALC_after) ~ (ALC_before + ALC_after)/2,
                    !is.na(ALC_before) ~ ALC_before,
                    TRUE ~ ALC_after),
  ) %>%
  select(id, date, day, all_of(list_absolute_counts))

tib_test <- tib_flow_all %>%
  filter(!is.na(day)) %>%
  inner_join(tib_absolute, by = c("id", "date", "day")) %>%
  arrange(id, day)

tib_test_expanded <- tib_flow_all %>%
  filter(!is.na(day)) %>%
  inner_join(tib_absolute_expanded, by = c("id", "date", "day")) %>%
  arrange(id, day)

```

# Combining Data

```{r Final - Data, Grouped}
fun_datify <- function(tib_data) {return(tib_data %>% filter(day <= 30 | is.na(day)))}

tib_data_all <- tib_patients_all %>% 
  full_join(tib_sfratio_all, by = "id") %>%
  full_join(tib_cytokine_all, by = list_id) %>%
  full_join(tib_flow_all, by = list_id) %>%
  full_join(tib_elisa_all, by = list_id) %>%
  full_join(tib_elispot_all, by = list_id) %>%
  full_join(tib_viral_all, by = list_id) %>%
  full_join(tib_labs_all, by = list_id) %>%
  full_join(tib_vitals_all, by = list_id) %>%
  full_join(tib_vitd_all, by = list_id)

tib_included_patients <- tib_patients_all %>%
  select(id, healthy, basic_include, Tocilizumab, convrecip) %>%
  mutate(
    has_labs = id %in% tib_labs_all$id,
    has_vitals = id %in% tib_vitals_all$id,
    has_sfratio = id %in% tib_sfratio_all$id,
    
    has_cyto = id %in% tib_cytokine_all$id,
    use_cyto = ((healthy | (basic_include & !Tocilizumab)) & has_cyto),
    
    has_flow = id %in% tib_flow_all$id,
    use_flow = ((healthy | basic_include) & has_flow),
    
    has_elisa = id %in% tib_elisa_all$id,
    use_elisa = ((healthy | (basic_include & !convrecip)) & has_elisa),
    
    has_elispot = id %in% tib_elispot_all$id,
    use_elispot = ((healthy | basic_include) & has_elispot),
    
    has_viral = id %in% tib_viral_all$id,
    use_viral = ((healthy | basic_include) & has_viral),
    
    has_vitd = id %in% tib_vitd_all$id,
    use_vitd = ((healthy | basic_include) & has_vitd)
  ) %>%
  filter(use_cyto | use_flow | use_elisa | use_elispot | use_viral | use_vitd) %>%
  select(-basic_include, -Tocilizumab, -convrecip) %>%
  select(id, healthy, has_labs, has_vitals, has_sfratio, starts_with("use"))

get_included <- function(tib_data, str_assay = "none") {
  tib_include <- tib_included_patients
  if (str_assay != "none") {
    tib_include <- tib_include %>%
      filter(!!as.symbol(paste0("use_", str_assay)))
    
  }
  inner_join(tib_include %>% select(id), tib_data, by = "id") %>%
    return()
}

get_included_days <- function(tib_data, str_assay = "none") {
   get_included(tib_data, str_assay) %>%
    select(all_of(list_id)) %>%
    return()
}

tib_id_day <- bind_rows(
  get_included_days(fun_datify(tib_cytokine_all), "cyto"),
  get_included_days(fun_datify(tib_flow_all), "flow"),
  get_included_days(tib_elisa_all, "elisa"),
  get_included_days(fun_datify(tib_elispot_all), "elispot"),
  get_included_days(fun_datify(tib_viral_all), "viral"),
  get_included_days(tib_labs_all),
  get_included_days(tib_vitals_all),
  get_included_days(tib_sfratio_all),
  get_included_days(tib_vitd_all)
) %>% unique()


tib_data_include <- tib_id_day %>%
  full_join(get_included(fun_datify(tib_cytokine_all), "cyto"), by = list_id) %>%
  full_join(get_included(fun_datify(tib_flow_all), "flow"), by = list_id) %>%
  full_join(get_included(tib_elisa_all, "elisa"), by = list_id) %>%
  full_join(get_included(fun_datify(tib_elispot_all), "elispot"), by = list_id) %>%
  full_join(get_included(fun_datify(tib_viral_all), "viral"), by = list_id) %>%
  full_join(get_included(tib_labs_all), by = list_id) %>%
  full_join(get_included(tib_vitals_all), by = list_id) %>%
  full_join(get_included(tib_sfratio_all), by = list_id) %>%
  full_join(get_included(tib_vitd_all), by = list_id) %>%
  left_join(tib_patients_all, by = "id") %>%
  left_join(tib_included_patients %>% select(-healthy), by = "id") %>%
  relocate(all_of(c(colnames(tib_included_patients), colnames(tib_patients_all))))

fun_group <- function(tib_data, suffix, rename) {
  if (length(tib_data$id) == 0) {
    return(tibble())
  }
  if(rename) {
    columns_to_use <- tib_columns %>%
      filter(variable %in% colnames(tib_data))
  }
  else {
    columns_to_use <- tib_columns %>%
      filter(name %in% colnames(tib_data))
  }
  list_funs <- list(
    max = ~max(.x, na.rm = TRUE),
    min = ~min(.x, na.rm = TRUE),
    mean = ~mean(.x, na.rm = TRUE),
    first = ~first(na.omit(.x))
  )
  list_suffix <- list(
    max = " (Max)",
    min = " (Min)",
    mean = " (Mean)",
    first = ""
  )
  tib_return <- select(tib_data, id) %>% unique()
  for(fun in names(list_funs)) {
    list_fun <- columns_to_use %>%
      filter(!!as.symbol(fun)) %>% pull(variable)
    if(length(list_fun) > 0) {
      if(rename) {
        tib_fun <- tib_data %>%
          group_by(id) %>%
          summarise(across(all_of(list_fun), list_funs[fun])) %>%
          mutate(across(everything(), ~ifelse(is.infinite(.x), NA_real_, .x)))
        colnames(tib_fun) <- c("id",
          tibble(variable = list_fun) %>% left_join(columns_to_use, by = "variable") %>%
          mutate(suf = ifelse(suffix, list_suffix[fun], "")) %>%
          unite(name, name, suf, sep = "") %>%
          pull(name))
      }
      else {
        list_fun <- columns_to_use %>%
          filter(!!as.symbol(fun)) %>% pull(name) %>% unique()
        tib_fun <- tib_data %>%
          group_by(id) %>%
          summarise(across(all_of(list_fun), list_funs[fun])) %>%
          mutate(across(everything(), ~ifelse(is.infinite(.x), NA_real_, .x)))
        colnames(tib_fun) <- c("id", lapply(list_fun, function(x) {return(paste0(x, ifelse(suffix, list_suffix[fun], "")))}))
      }
      tib_return <- tib_return %>%
        left_join(tib_fun, by = "id")
    }
  }
  
  return(tib_return)
}

fun_triple_group <- function(tib_data, suffix = FALSE, rename = TRUE) {
  if("day" %in% colnames(tib_data)) {
    bind_rows(
      fun_group(tib_data %>% filter(day <= 9, !is.na(day)), suffix, rename) %>% mutate(time_group = "D0-9"),
      fun_group(tib_data %>% filter(day >= 10, day <= 30, !is.na(day)), suffix, rename) %>% mutate(time_group = "D10-30"),
      fun_group(tib_data %>% filter(day >= 0, day <= 30, !is.na(day)), suffix, rename) %>% mutate(time_group = "D0-30"),
      fun_group(tib_data %>% filter(is.na(day)), suffix, rename) %>% mutate(time_group = "Healthy")
    ) %>%
      return()
  }
  else {
    bind_rows(
      fun_group(tib_data %>% filter(!is.na(healthy)), suffix, rename) %>% mutate(time_group = "D0-9"),
      fun_group(tib_data %>% filter(!is.na(healthy)), suffix, rename) %>% mutate(time_group = "D10-30"),
      fun_group(tib_data %>% filter(!is.na(healthy)), suffix, rename) %>% mutate(time_group = "D0-30"),
      fun_group(tib_data %>% filter(healthy), suffix, rename) %>% mutate(time_group = "Healthy")
    ) %>%
      return()
  }
}

list_group_id = c("id", "time_group")

tib_data_include_grouped <- bind_rows(
  tib_data_include %>% filter(day <= 30 & !healthy) %>% select(id) %>% unique() %>%
    full_join(tibble(time_group = c("D0-9", "D10-30", "D0-30")), by = character()),
  tib_data_include %>% filter(healthy) %>% select(id) %>% unique() %>%
    mutate(time_group = "Healthy")
  ) %>%
  relocate(time_group) %>%
  left_join(fun_triple_group(get_included(tib_patients_all)), by = list_group_id) %>%
  full_join(fun_triple_group(get_included(fun_datify(tib_cytokine_all), "cyto")), by = list_group_id) %>%
  full_join(fun_triple_group(get_included(fun_datify(tib_flow_all), "flow")), by = list_group_id) %>%
  full_join(fun_triple_group(get_included(fun_datify(tib_elisa_all), "elisa")), by = list_group_id) %>%
  full_join(fun_triple_group(get_included(fun_datify(tib_elispot_all), "elispot")), by = list_group_id) %>%
  full_join(fun_triple_group(get_included(fun_datify(tib_viral_all), "viral")), by = list_group_id) %>%
  full_join(fun_triple_group(get_included(fun_datify(tib_labs_all)), TRUE, FALSE), by = list_group_id) %>%
  full_join(fun_triple_group(get_included(fun_datify(tib_vitals_all)), TRUE), by = list_group_id) %>%
  relocate(time_group)

rm(tib_id_day)
rm(list_group_id)

triple_save <- function(str_name, tib_data) {
  tib_data %>%
    writexl::write_xlsx(paste0(STR_DATA_DIR_OTHER, paste0(str_name, "_data.xlsx")))
  tib_data %>%
    write_csv(paste0(STR_DATA_DIR_OTHER, paste0(str_name, "_data.csv")))
  tib_data %>%
    saveRDS(paste0(STR_DATA_DIR_OTHER, paste0(str_name, "_data.rds")))
}

triple_save("all", tib_data_include_grouped)

tib_data_all %>%
  writexl::write_xlsx(paste0(STR_DATA_DIR_OTHER, "everything.xlsx"))

tib_included_patients %>%
  writexl::write_xlsx(paste0(STR_DATA_DIR_OTHER, "included_patients.xlsx"))
```

```{r Final - Data, Demographics Table}
# Adding in ICS patients, 579 counted as not healthy for this - relabeling as 579C
tib_demo <- tib_included_patients %>%
  bind_rows(
    tibble(id = c("579", "453", "581")) %>% full_join(
      tib_included_patients %>%
        filter(id == "579") %>%
        select(-id) %>%
        mutate(across(everything(), ~ifelse(.x, FALSE, .x))),
    by = character()) %>%
      mutate(healthy = (id != "579"))
  ) %>%
  left_join(tib_patients_all %>% select(-healthy), by = "id") %>%
  mutate(
    id = ifelse((id == "579") & !healthy, "579C", id),
    sfseverity_highest = factor(ifelse((id == "579C"), "Mild", as.character(sfseverity_highest)), levels = sflevels(TRUE, TRUE)),
    sfratio_lowest = ifelse((id == "579C"), 10000.0/21.0, sfratio_lowest),
    HTN = pmh_htn,
    `CAD or PAD` = ifelse(pmh_cad == 1 | pmh_pad == 1, 1, 0),
    `COPD or Asthma` = ifelse(pmh_copd == 1 | pmh_asthma == 1, 1, 0),
    Diabetes = pmh_dm,
    ESRD = pmh_esrd,
    dead_admission = ifelse(is.na(death_date), FALSE, death_date <= discharge_date)*1,
    dead_30 = ifelse(is.na(death_date), FALSE, death_date <= as_date(d0) %m+% period("30 days"))*1,
    dead_60 = ifelse(is.na(death_date), FALSE, death_date <= as_date(d0) %m+% period("60 days"))*1
  )


tib_demo_table <- bind_rows(
  bind_cols(
    tibble(Row = "Number of Patients"),
    tib_demo %>% group_by(sfseverity_highest) %>%
      summarise(n = as.character(n())) %>%
      spread(sfseverity_highest, n),
    tib_demo %>%
      filter(!healthy) %>%
      summarise(Total = as.character(n())),
    tibble(p.value = NA_real_)
  ),
  bind_cols(
    tibble(Row = "Age (years)"),
    tib_demo %>% group_by(sfseverity_highest) %>%
      summarise(meanage = round(mean(floor(age_d0), na.rm = TRUE), digits = 1),
                minage = min(floor(age_d0), na.rm = TRUE),
                maxage = max(floor(age_d0), na.rm = TRUE)) %>%
      mutate(age = paste0(meanage, " (", minage, "-", maxage, ")")) %>%
      select(sfseverity_highest, age) %>%
      spread(sfseverity_highest, age),
    tib_demo %>%
      filter(!healthy) %>%
      summarise(meanage = round(mean(floor(age_d0), na.rm = TRUE), digits = 1),
                minage = min(floor(age_d0), na.rm = TRUE),
                maxage = max(floor(age_d0), na.rm = TRUE)) %>%
      mutate(Total = paste0(meanage, " (", minage, "-", maxage, ")")) %>%
      select(Total),
    tib_demo %>% select(sfseverity_highest, age_d0) %>% filter(!is.na(age_d0), sfseverity_highest %in% c("Mild", "Severe")) %>%
      wilcox.test(age_d0 ~ sfseverity_highest, data = ., ) %>% tidy() %>% select(p.value)
  ),
  bind_cols(
    tibble(Row = "Sex (% Male)"),
    tib_demo %>% select(sfseverity_highest, sex) %>%
      group_by(sfseverity_highest) %>%
      mutate(total = n()) %>%
      group_by(sfseverity_highest, sex) %>%
      summarise(pct = round(n()/total*100.0, 1),
                n = n()) %>% unique() %>%
      ungroup() %>% mutate(n = paste0(pct, " (", n, ")")) %>%
      filter(sex == "M") %>% select(sfseverity_highest, n) %>%
      spread(sfseverity_highest, n),
    tib_demo %>% filter(!healthy) %>%
      mutate(total = n()) %>%
      group_by(sex) %>%
      summarise(pct = round(n()/total*100.0, 1),
                n = n()) %>% unique() %>%
      mutate(Total = paste0(pct, " (", n, ")")) %>%
      filter(sex == "M") %>% ungroup() %>% select(Total),
    tib_demo %>% group_by(sfseverity_highest, sex) %>% filter(!is.na(sex), sfseverity_highest %in% c("Mild", "Severe")) %>%
      summarise(n = n()) %>% spread(sfseverity_highest, n) %>% select(-sex) %>% as.matrix() %>% fisher_test() %>% select(p.value = p)
  ),
  bind_cols(
    tib_demo %>% mutate(
        Row = case_when(
          !grepl("not|declined|unknown", ethnic, ignore.case = TRUE) & !is.na(ethnic) ~ ethnic,
          grepl("declined|unknown", race, ignore.case = TRUE) | is.na(race) ~ "Did not disclose/unknown",
          TRUE ~ race
        )) %>% select(sfseverity_highest, Row) %>%
      group_by(sfseverity_highest) %>%
      mutate(total = n()) %>%
      group_by(sfseverity_highest, Row) %>%
      summarise(pct = round(n()/total*100.0, 1),
                n = n()) %>% unique() %>%
      ungroup() %>% mutate(n = paste0(pct, " (", n, ")")) %>% select(-pct) %>%
      spread(sfseverity_highest, n) %>%
      mutate(across(everything(), ~replace_na(.x,"0 (0)"))),
    tib_demo %>% mutate(
        Row = case_when(
          !grepl("not|declined|unknown", ethnic, ignore.case = TRUE) & !is.na(ethnic) ~ ethnic,
          grepl("declined|unknown", race, ignore.case = TRUE) | is.na(race) ~ "Did not disclose/unknown",
          TRUE ~ race
        )) %>% select(Row) %>%
      mutate(total = n()) %>%
      group_by(Row) %>%
      summarise(pct = round(n()/total*100.0, 1),
                n = n()) %>% unique() %>%
      ungroup() %>% mutate(Total = paste0(pct, " (", n, ")")) %>%
      select(Total),
    tib_demo %>% mutate(
        Row = case_when(
          !grepl("not|declined|unknown", ethnic, ignore.case = TRUE) & !is.na(ethnic) ~ ethnic,
          grepl("declined|unknown", race, ignore.case = TRUE) | is.na(race) ~ "Did not disclose/unknown",
          TRUE ~ race
        )) %>% group_by(sfseverity_highest, Row) %>% filter(sfseverity_highest %in% c("Mild", "Severe")) %>%
      summarise(n = n()) %>% spread(sfseverity_highest, n) %>% mutate(Severe = replace_na(Severe, 0)) %>%
      select(-Row) %>% as.matrix() %>% row_wise_fisher_test() %>% select(p.value = p)
  ),
  bind_cols(
    tibble(Row = "Percent Outpatient or Discharged from ED", Healthy = NA_character_,
           Moderate = "0 (0)", Severe = "0 (0)"),
    tib_demo %>% filter(!healthy) %>%
      mutate(outpt = is.na(admit_date)) %>%
      select(sfseverity_highest, outpt) %>%
      group_by(sfseverity_highest) %>%
      mutate(total = n()) %>%
      group_by(sfseverity_highest, outpt) %>%
      summarise(pct = round(n()/total*100.0, 1),
                n = n()) %>% unique() %>%
      ungroup() %>% mutate(n = paste0(pct, " (", n, ")")) %>%
      filter(outpt) %>% select(sfseverity_highest, n) %>%
      spread(sfseverity_highest, n),
    tib_demo %>% filter(!healthy) %>%
      mutate(outpt = is.na(admit_date)) %>%
      mutate(total = n()) %>%
      group_by(outpt) %>%
      summarise(pct = round(n()/total*100.0, 1),
                n = n()) %>% unique() %>%
      mutate(Total = paste0(pct, " (", n, ")")) %>%
      filter(outpt) %>% ungroup() %>% select(Total),
    tib_demo %>% filter(sfseverity_highest %in% c("Mild", "Severe")) %>%
      mutate(outpt = is.na(admit_date)) %>% group_by(sfseverity_highest, outpt) %>%
      summarise(n = n()) %>% spread(sfseverity_highest, n) %>% mutate(Severe = replace_na(Severe, 0)) %>%
      select(-outpt) %>% as.matrix() %>% fisher_test() %>% select(p.value = p)
  ),
  bind_cols(
    tibble(Row = "Mean Length of Stay for Hospitalized Patients (Days)", Healthy = NA_character_),
    tib_demo %>% filter(!healthy) %>%
      group_by(sfseverity_highest) %>%
      summarise(meanal = round(mean(admission_length, na.rm = TRUE), digits = 1),
                minal = min(admission_length, na.rm = TRUE),
                maxal = max(admission_length, na.rm = TRUE)) %>%
      mutate(len = paste0(meanal, " (", minal, "-", maxal, ")")) %>%
      select(sfseverity_highest, len) %>%
      spread(sfseverity_highest, len),
    tib_demo %>%
      filter(!healthy) %>%
      summarise(meanal = round(mean(admission_length, na.rm = TRUE), digits = 1),
                minal = min(admission_length, na.rm = TRUE),
                maxal = max(admission_length, na.rm = TRUE)) %>%
      mutate(Total = paste0(meanal, " (", minal, "-", maxal, ")")) %>%
      select(Total),
      tib_demo %>% select(sfseverity_highest, admission_length) %>% filter(!is.na(admission_length), sfseverity_highest %in% c("Mild", "Severe")) %>%
        wilcox.test(admission_length ~ sfseverity_highest, data = ., ) %>% tidy() %>% select(p.value)
  ),
  # bind_cols(
  #   tibble(Row = "Medications Received", Healthy = NA_character_),
  #   tib_demo %>% filter(!healthy) %>%
  #     group_by(sfseverity_highest) %>%
  #     mutate(nmeds = Remdesivir + Tocilizumab + Steroid + Azithromycin + `Lopinavir/Ritonavir`) %>%
  #     summarise(meanmeds = round(mean(nmeds),1),
  #               minmeds = min(nmeds),
  #               maxmeds = max(nmeds)) %>%
  #     mutate(len = paste0(meanmeds, " (", minmeds, "-", maxmeds, ")")) %>%
  #     select(sfseverity_highest, len) %>%
  #     spread(sfseverity_highest, len),
  #   tib_demo %>%
  #     filter(!healthy) %>%
  #     mutate(nmeds = Remdesivir + Tocilizumab + Steroid + Azithromycin + `Lopinavir/Ritonavir`) %>%
  #     summarise(meanmeds = round(mean(nmeds),1),
  #               minmeds = min(nmeds),
  #               maxmeds = max(nmeds)) %>%
  #     mutate(Total = paste0(meanmeds, " (", minmeds, "-", maxmeds, ")")) %>%
  #     select(Total)
  # ),
  bind_cols(
    tibble(Healthy = NA_character_),
    tib_demo %>% filter(!healthy) %>%
      select(id, sfseverity_highest, Remdesivir, Tocilizumab, Steroid, Azithromycin, `Lopinavir/Ritonavir`) %>%
      gather(Row, val, Remdesivir, Tocilizumab, Steroid, Azithromycin, `Lopinavir/Ritonavir`) %>%
      mutate(val = ifelse(val, 1, 0), total = 1) %>%
      group_by(sfseverity_highest, Row) %>%
      summarise(pct = round(sum(val)/sum(total)*100.0, 1),
                n = sum(val)) %>% unique() %>%
      ungroup() %>% mutate(n = paste0(pct, " (", n, ")")) %>% select(-pct) %>%
      spread(sfseverity_highest, n),
    tib_demo %>% filter(!healthy) %>%
      select(id, sfseverity_highest, Remdesivir, Tocilizumab, Steroid, Azithromycin, `Lopinavir/Ritonavir`) %>%
      gather(Row, val, Remdesivir, Tocilizumab, Steroid, Azithromycin, `Lopinavir/Ritonavir`) %>%
      mutate(val = ifelse(val, 1, 0), total = 1) %>%
      group_by(Row) %>%
      summarise(pct = round(sum(val)/sum(total)*100.0, 1),
                n = sum(val)) %>% unique() %>%
      ungroup() %>% mutate(Total = paste0(pct, " (", n, ")")) %>%
      select(Total),
    tib_demo %>% filter(sfseverity_highest %in% c("Mild", "Severe")) %>% 
      select(id, sfseverity_highest, Remdesivir, Tocilizumab, Steroid, Azithromycin, `Lopinavir/Ritonavir`) %>%
      gather(Row, val, Remdesivir, Tocilizumab, Steroid, Azithromycin, `Lopinavir/Ritonavir`) %>%
      mutate(val = ifelse(val, 1, 0)) %>%
      group_by(sfseverity_highest, Row) %>%
      summarise(n = sum(val)) %>% spread(sfseverity_highest, n) %>% mutate(Severe = replace_na(Severe, 0)) %>%
      select(-Row) %>% as.matrix() %>% row_wise_fisher_test() %>% select(p.value = p)
  ),
  bind_cols(
    tibble(Healthy = NA_character_),
    tib_demo %>% filter(!healthy) %>%
      select(id, sfseverity_highest, HTN, `CAD or PAD`, `COPD or Asthma`, Diabetes, `ESRD`) %>%
      gather(Row, val, HTN, `CAD or PAD`, `COPD or Asthma`, Diabetes, `ESRD`) %>%
      mutate(val = ifelse(val, 1, 0), total = 1) %>%
      group_by(sfseverity_highest, Row) %>%
      summarise(pct = round(sum(val)/sum(total)*100.0, 1),
                n = sum(val)) %>% unique() %>%
      ungroup() %>% mutate(n = paste0(pct, " (", n, ")")) %>% select(-pct) %>%
      spread(sfseverity_highest, n),
    tib_demo %>% filter(!healthy) %>%
      select(id, sfseverity_highest, HTN, `CAD or PAD`, `COPD or Asthma`, Diabetes, `ESRD`) %>%
      gather(Row, val, HTN, `CAD or PAD`, `COPD or Asthma`, Diabetes, `ESRD`) %>%
      mutate(val = ifelse(val, 1, 0), total = 1) %>%
      group_by(Row) %>%
      summarise(pct = round(sum(val)/sum(total)*100.0, 1),
                n = sum(val)) %>% unique() %>%
      ungroup() %>% mutate(Total = paste0(pct, " (", n, ")")) %>%
      select(Total),
    tib_demo %>% filter(sfseverity_highest %in% c("Mild", "Severe")) %>% 
      select(id, sfseverity_highest, HTN, `CAD or PAD`, `COPD or Asthma`, Diabetes, `ESRD`) %>%
      gather(Row, val, HTN, `CAD or PAD`, `COPD or Asthma`, Diabetes, `ESRD`) %>%
      mutate(val = ifelse(val, 1, 0)) %>%
      group_by(sfseverity_highest, Row) %>%
      summarise(n = sum(val)) %>% spread(sfseverity_highest, n) %>% mutate(Severe = replace_na(Severe, 0)) %>%
      select(-Row) %>% as.matrix() %>% row_wise_fisher_test() %>% select(p.value = p)
  ),
  bind_cols(
    tibble(Row = "Died During Index Admission (%)"),
    tib_demo %>% select(sfseverity_highest, dead_admission) %>%
      group_by(sfseverity_highest) %>%
      mutate(total = n()) %>%
      group_by(sfseverity_highest, dead_admission) %>%
      summarise(pct = round(n()/total*100.0, 1),
                n = n()) %>% unique() %>%
      ungroup() %>% mutate(n = paste0(pct, " (", n, ")")) %>%
      filter(dead_admission==1) %>% select(sfseverity_highest, n) %>%
      spread(sfseverity_highest, n),
    tib_demo %>% filter(!healthy) %>%
      mutate(total = n()) %>%
      group_by(dead_admission) %>%
      summarise(pct = round(n()/total*100.0, 1),
                n = n()) %>% unique() %>%
      mutate(Total = paste0(pct, " (", n, ")")) %>%
      filter(dead_admission==1) %>% ungroup() %>% select(Total),
#    tib_demo %>% group_by(sfseverity_highest, dead_admission) %>% filter(!is.na(dead_admission), sfseverity_highest %in% c("Mild", "Severe")) %>%
#      summarise(n = n()) %>% spread(sfseverity_highest, n) %>% select(-dead_admission) %>% as.matrix() %>% fisher_test() %>% select(p.value = p)
    tibble(p.value = NA)
  )
)


tib_demo %>%
  writexl::write_xlsx(paste0(STR_DATA_DIR_OTHER, "demographics_data.xlsx"))
tib_demo_table %>%
  writexl::write_xlsx(paste0(STR_DATA_DIR_OTHER, "demographics_table.xlsx"))
```

# Plotting

```{r SF Ratio - Plots}

########################
#       PLOTTING       #
########################

fun_plot_sf <- function(ratio) {
  sfname <- str_split(ratio, "_")[[1]][2]
  
  list_plots <- list()
  
  fun_plot_linesf <- function(subgroup = FALSE) {
    tib_data <- tib_data_include
    colors <- plotcolors(sfmatch = subgroup)
    str_title <- paste0("\nGrouped by ", str_to_title(sfname)," Severity")
    if(subgroup != FALSE){
      tib_data <- tib_data_include %>%
        filter(!!as.symbol(ratio) == subgroup)
      str_title <- subgroup
    }

    plot_sf <- tib_data %>%
      filter(!is.na(sfratio_mean)) %>%
      ggplot(aes_string(x = "day", y = "sfratio_mean", group = "id", colour = ratio)) +
        theme_bw() +
        geom_line() +
        scale_colour_manual(values = colors) +
        guides(color = FALSE, fill = FALSE) + 
        labs(color = paste0(str_to_title(sfname), " Severity"),
             title = paste0("SF Ratio by Day, ", str_title)) +
        ylab("SF Ratio") + xlab("DPSO") +
        theme(axis.title.y = element_text(size = INT_SIG_SIZE*4.5),
              axis.text.y = element_text(size = INT_SIG_SIZE*4),
              title = element_text(size = INT_SIG_SIZE*4.5))
    suffix <- ""
    if(subgroup != FALSE) {
      suffix <- paste0("-", str_to_lower(subgroup))
    }
    ggsave(paste0(STR_PLOT_DIR_CLINICAL, "sf-", sfname , "severity-scatter-line", suffix, ".svg"),
           plot_sf, width = INT_FIG_WIDTH, height = INT_FIG_HEIGHT)
    return(list(plot_sf))
  }
  
  list_plots[paste0(sfname, "-scatter_all")] <- fun_plot_linesf()
  list_plots[paste0(sfname, "-scatter_severe")] <- fun_plot_linesf("Severe")
  list_plots[paste0(sfname, "-scatter_moderate")] <- fun_plot_linesf("Moderate")
  list_plots[paste0(sfname, "-scatter_mild")] <- fun_plot_linesf("Mild")
  
  fun_plot_barsf <- function(pos) {
    plot_fill <- tib_data_include %>%
      filter(!is.na(day)) %>%
      ggplot(aes_string(x = "day", fill = ratio, y = 1)) +
        theme_bw() +
        geom_bar(position = pos, stat = "identity") +
        scale_fill_manual(values = plotcolors()) +
        {if(pos == "fill") scale_y_continuous(labels = scales::percent_format())} +
        guides(color = FALSE, fill = FALSE) + 
        labs(fill = paste0(str_to_title(sfname), " Severity"),
             title = paste0(ifelse(pos == "fill", "Percent of ", ""),
                            "Patients by Day,\nGrouped by ", str_to_title(sfname)," Severity")) +
        ylab(paste0(ifelse(pos == "fill", "Percent of ", ""), "Patients")) + xlab("DPSO") + 
        theme(axis.title.y = element_text(size = INT_SIG_SIZE*4.5),
              axis.text.y = element_text(size = INT_SIG_SIZE*4),
              title = element_text(size = INT_SIG_SIZE*4.5))
    ggsave(paste0(STR_PLOT_DIR_CLINICAL, "sf-", sfname, "severity-bar-", pos, ".svg"),
           plot_fill, width = INT_FIG_WIDTH, height = INT_FIG_HEIGHT)
    return(list(plot_fill))
  }
  
  list_plots[paste0(sfname, "-bar-stack")] <- fun_plot_barsf("stack")
  list_plots[paste0(sfname, "-bar-fill")] <- fun_plot_barsf("fill")
  
  plot_stack_admission <- tib_data_include %>%
    select(id, admission_length, all_of(ratio)) %>%
    filter(!is.na(admission_length)) %>%
    unique() %>%
    ggplot(aes_string(x = "reorder(id, admission_length)", y = "admission_length", fill = ratio)) +
      theme_bw() +
      geom_col() +
      scale_fill_manual(values = plotcolors()) +
      guides(color = FALSE, fill = FALSE) + 
      labs(fill = paste0(str_to_title(sfname), " Severity"),
           title = paste0("Admission Length,\nGrouped by ", str_to_title(sfname)," Severity")) +
      ylab("Length of Admission") +
      theme(axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.title.x = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(), title = element_text(size = INT_SIG_SIZE*4.5))
  ggsave(paste0(STR_PLOT_DIR_CLINICAL, "sf-", sfname, "severity-admitlength-bar.svg"),
         plot_stack_admission, width = INT_FIG_WIDTH, height = INT_FIG_HEIGHT)
  list_plots[paste0(sfname, "-admitlength")] <- list(plot_stack_admission)
  return(list_plots)
}

list_plots <- fun_plot_sf("sfseverity_highest")

oxygen_devices <- list(expression("Room\nAir"), expression(""<="6L O"[2]),
                     expression("CPAP,\nBipap,\nHFNC"), expression("Ventilator"))

fun_plot_box_sfoxygen <- function() {
  tib_plot <- tib_sfratio_devices %>%
    right_join(tib_included_patients, by = "id") %>%
    filter(!is.na(device_group), !healthy)
  plot_one <- tib_plot %>%
    ggplot(aes(x = fct_rev(device_group), y = sfratio)) +
    theme_bw() +
    # Box plot with jitter
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(width = 0.1, size = 0.1) +
    # Labels
    labs(title = "SF Ratio by Oxygen Delivery") + ylab("SF Ratio") +
    theme(axis.title.y = element_blank()) +
    scale_x_discrete(labels=c(oxygen_devices[[4]], oxygen_devices[[3]], oxygen_devices[[2]], oxygen_devices[[1]])) +
    coord_flip()+
theme(axis.text.y = element_text(size = INT_SIG_SIZE*3, hjust = 0.5), title = element_text(size = INT_SIG_SIZE*4.5))
  return(list(plot_one))
}

plot_box_sfoxygen <- fun_plot_box_sfoxygen()
ggsave(paste0(STR_PLOT_DIR_CLINICAL, "sf-to-oxygenmode.svg"),
       plot_box_sfoxygen[[1]], width = INT_FIG_WIDTH, height = INT_FIG_HEIGHT)
list_plots["sf-to-oxygen"] <- plot_box_sfoxygen

int_spo2_max <- 100
int_spo2_min <- 75
tib_sf_ranges <- tibble(fio2 = seq(21,100,by=0.1)) %>%
  mutate(
    spo2_max = int_spo2_max,
    spo2_high = SF_BREAKS[3]*fio2/100.0,
    spo2_low = SF_BREAKS[2]*fio2/100.0,
    spo2_high = ifelse(spo2_high < int_spo2_min, int_spo2_min, ifelse(spo2_high > int_spo2_max, int_spo2_max, spo2_high)),
    spo2_low = ifelse(spo2_low < int_spo2_min, int_spo2_min, ifelse(spo2_low > int_spo2_max, int_spo2_max, spo2_low)),
    spo2_min = int_spo2_min,
  )

plot_scatter_fio2_spo2 <- tib_sfratio_devices %>% group_by(id, day) %>% 
  summarise(sfratio = mean(sfratio), fio2 = mean(fio2), spo2 = mean(spo2)) %>%
  mutate(sfseverity = cut(sfratio, breaks = SF_BREAKS, labels = sflevels(), right = FALSE)) %>% ggplot() +
  theme_bw() +
  geom_ribbon(data = tib_sf_ranges, aes(x = fio2, ymin=spo2_min,ymax=spo2_low), fill=plotcolors(sfmatch = "Severe"), alpha=0.2) +
  geom_ribbon(data = tib_sf_ranges, aes(x = fio2, ymin=spo2_high,ymax=spo2_low), fill=plotcolors(sfmatch = "Moderate"), alpha=0.2) +
  geom_ribbon(data = tib_sf_ranges, aes(x = fio2, ymin=spo2_max,ymax=spo2_high), fill=plotcolors(sfmatch = "Mild"), alpha=0.2) +
  geom_point(aes(fio2, spo2, color = sfseverity), size = INT_SIG_SIZE/2) +
  scale_color_manual(values = plotcolors()) +
  guides(color = FALSE, fill = FALSE) +
  theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  xlab(expression("FiO"[2])) + ylab(expression("SpO"[2])) +
  ylim(int_spo2_min, int_spo2_max)
ggsave(paste0(STR_PLOT_DIR_CLINICAL, "fio2_spo2.svg"),
       plot_scatter_fio2_spo2, width = INT_FIG_WIDTH, height = INT_FIG_HEIGHT)
list_plots["fio2_spo2"] <- list(plot_scatter_fio2_spo2)

plot_scatter_fio2_spo2 <- tib_sfratio_devices %>% group_by(id, day) %>% 
  summarise(sfratio = mean(sfratio), fio2 = mean(fio2), spo2 = mean(spo2)) %>%
  left_join(tib_patients_all %>% select(id, sfseverity = sfseverity_highest)) %>% ggplot() +
  theme_bw() +
  geom_ribbon(data = tib_sf_ranges, aes(x = fio2, ymin=spo2_min,ymax=spo2_low), fill=plotcolors(sfmatch = "Severe"), alpha=0.2) +
  geom_ribbon(data = tib_sf_ranges, aes(x = fio2, ymin=spo2_high,ymax=spo2_low), fill=plotcolors(sfmatch = "Moderate"), alpha=0.2) +
  geom_ribbon(data = tib_sf_ranges, aes(x = fio2, ymin=spo2_max,ymax=spo2_high), fill=plotcolors(sfmatch = "Mild"), alpha=0.2) +
  geom_point(aes(fio2, spo2, color = sfseverity), size = INT_SIG_SIZE/2) +
  scale_color_manual(values = plotcolors()) +
  guides(color = FALSE, fill = FALSE) +
  theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  xlab(expression("FiO"[2])) + ylab(expression("SpO"[2])) +
  ylim(int_spo2_min, int_spo2_max)
ggsave(paste0(STR_PLOT_DIR_CLINICAL, "fio2_spo2_overallseverity.svg"),
       plot_scatter_fio2_spo2, width = INT_FIG_WIDTH, height = INT_FIG_HEIGHT)
list_plots["fio2_spo2_severity"] <- list(plot_scatter_fio2_spo2)

list_plots %>%
  saveRDS(paste0(STR_PLOT_DIR_CLINICAL, "clinical.rds"))

```

```{r Cytokine - Plotting}

list_daygroups <- c("Days 1-9", "Days 10-30", NA_character_)

daycut <- function(var) {
  return(cut(var, breaks = c(-1,9,30,Inf), labels = list_daygroups))
}

########################
#       PLOTTING       #
########################
fun_assay_select <- function(assay, healthy = TRUE, fun = "max") {
  list_funs <- list(
    "max" = max,
    "mean" = mean
    )
  tib_selected <- tib_data_include %>%
    mutate(
      time_group = daycut(day)
    ) %>%
    select(
      time_group,
      result = assay,
      sfseverity_highest,
      sfratio_lowest,
      id,
      day,
      healthy
    ) %>%
    # Remove N/A value results
    filter(
      !is.na(result) &
      !is.nan(result)
    )

  tib_assay <- tib_selected %>%
      filter(
        !is.na(sfseverity_highest),
        !is.na(time_group),
        !is.na(day)
      ) %>%
      group_by(
        time_group,
        sfseverity_highest,
        id
      ) %>%
      summarise(result = list_funs[[fun]](result))
  if(healthy) {
    list(
      tib_assay,
      tib_selected %>%
        filter(healthy) %>%
        select(id, result) %>%
        mutate(sfseverity_highest = "Healthy")
    ) %>%
      return()
  }
  else {
    return(tib_assay)
  }
}

# Box plots of cytokine data
fun_plot_facet_box <- function(assay, yl, title, logscale = FALSE, fun = "max"){
  # Creating additional factor level for healthy patients
  
  # Calling fun_cytokine_select to filter and process QC for selected cytokine
  tib_plot <- fun_assay_select(assay, fun = fun)

  tib_plot <- tib_plot[[1]] %>%
    bind_rows(tib_plot[[2]] %>% mutate(time_group = list_daygroups[1])) %>%
    bind_rows(tib_plot[[2]] %>% mutate(time_group = list_daygroups[2])) %>%
    group_by(id, time_group, sfseverity_highest) %>%
    mutate(
      sfseverity_highest = factor(sfseverity_highest, sflevels(TRUE, TRUE)),
      time_group = factor(time_group, levels = list_daygroups)
    ) %>%
    filter(!is.na(time_group))
  
  if (logscale) {
    tib_plot <- tib_plot %>%
      filter(result >= 0)
  }

  # Tallying N per group for purposes of labeling, duplicating due to quirk of writing a label per group
  tib_ns <- tib_plot %>%
    group_by(time_group, sfseverity_highest) %>%
    select(time_group, sfseverity_highest, id) %>%
    arrange(sfseverity_highest) %>%
    unique() %>%
    summarise(ns = n()) %>%
    unite(column, c(sfseverity_highest, time_group), sep = ", ") %>%
    spread(column, ns) %>%
    mutate(Assay = assay) %>%
    relocate(Assay)

  # p-value comparison pairings
  comparisons_1 <- list(
    c(sflevels(TRUE, TRUE)[1], sflevels(TRUE, TRUE)[2]),
    c(sflevels(TRUE, TRUE)[2], sflevels(TRUE, TRUE)[3]),
    c(sflevels(TRUE, TRUE)[3], sflevels(TRUE, TRUE)[4])
  )

  comparisons_2 <- list(
    c(sflevels(TRUE, TRUE)[1], sflevels(TRUE, TRUE)[3])
  )

  comparisons_3 <- list(
    c(sflevels(TRUE, TRUE)[2], sflevels(TRUE, TRUE)[4])
  )

  comparisons_4 <- list(
    c(sflevels(TRUE, TRUE)[1], sflevels(TRUE, TRUE)[4])
  )

  plot_one <- tib_plot %>%
    ggplot(aes(x = sfseverity_highest, y = result, color = sfseverity_highest)) +
    theme_bw() +
    # Box plot with jitter
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(width = 0.1, size = INT_SIG_SIZE) +
    # p-values from above
    geom_signif(aes(x = sfseverity_highest, y = result, color = sfseverity_highest), comparisons = comparisons_1, color = "black", map_signif_level = fun_significance, margin_top = 0.05, textsize = INT_SIG_SIZE) +
    geom_signif(aes(x = sfseverity_highest, y = result, color = sfseverity_highest), comparisons = comparisons_2, color = "black", map_signif_level = fun_significance, margin_top = 0.15, textsize = INT_SIG_SIZE) +
    geom_signif(aes(x = sfseverity_highest, y = result, color = sfseverity_highest), comparisons = comparisons_3, color = "black", map_signif_level = fun_significance, margin_top = 0.25, textsize = INT_SIG_SIZE) +
    geom_signif(aes(x = sfseverity_highest, y = result, color = sfseverity_highest), comparisons = comparisons_4, color = "black", map_signif_level = fun_significance, margin_top = 0.35, textsize = INT_SIG_SIZE) +
    # Labels
    labs(color = "Severity", title = title) + ylab(yl) +
    # Colors
    scale_colour_manual(values = rev(plotcolors())) +
    # Legend colors
    #guides(color = guide_legend(reverse = TRUE)) +
    guides(color = FALSE) +
    # Somewhat hacky way of showing N for each group at the time at -3% of the max value to ensure it shows up on the plot
    # Remove ticks and variable labels
    theme(axis.title.x=element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(),
          axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5)) + 
    {if (logscale) scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
            labels = trans_format("log10", math_format(10^.x)))} +
    {if (logscale) annotation_logticks(sides = "l") } + 
    facet_wrap(~time_group) + 
    theme(strip.text.x = element_text(size = INT_SIG_SIZE*4))
  return(list(plot_one, tib_ns))
}

fun_cytokine_title <- function(label) {
  label %>% str_replace("IFNa", "IFN\u03B1") %>%
    str_replace("IFNg", "IFN\u03B3") %>%
    str_replace("(Fa)$", "F\u03B1") %>%
    str_replace("(Ra)$", "R\u03B1") %>%
    str_replace("1a", "1\u03B1") %>%
    str_replace("1b", "1\u03B2") %>%
  return()
}

fun_cytokine_svg <- function(cytokine) {
  str_name <- cytokine %>%
    tolower() %>%
    str_replace_all("[:punct:]", "-") %>%
    str_replace_all(" ", "_")
  plot_ns <- fun_plot_facet_box(cytokine, "pg/mL", fun_cytokine_title(cytokine), TRUE)
  if(nrow(plot_ns[[1]]$data) == 0) {
    plot_ns[[1]] <- ggplot(data = data.frame()) + geom_blank()
  }
  ggsave(paste0(STR_PLOT_DIR_CYTOKINE, str_name, "-box.svg"), plot_ns[[1]], width = INT_FIG_WIDTH, height = INT_FIG_HEIGHT)
  return(plot_ns)
}

# Saves all plots
list_plots <- lapply(list_cytokines_all, fun_cytokine_svg)
get_lists <- function(list_stuff, index) {
  return(list_stuff[[index]])
}
tib_ns <- bind_rows(lapply(list_plots, get_lists, 2))
list_plots <- lapply(list_plots, get_lists, 1)
names(list_plots) <- list_cytokines_all
saveRDS(list_plots, paste0(STR_PLOT_DIR_CYTOKINE, "cytokine_plots.rds"))
writexl::write_xlsx(tib_ns, paste0(STR_PLOT_DIR_CYTOKINE, "cytokine_ns.xlsx"))

```

```{r Flow - Plotting}
########################
#       PLOTTING       #
########################

label_cd8 <- list(
  "CD8 TEMRA",
  "CD8 EM",
  "CD8 CM",
  "CD8 Naive",
  "CD8 CD38",
  "CD8 CD57",
  "CD8 CD161",
  "CD8 CD95",
  "CD8 Tim3",
  "CD8 PD1"
  )
label_cd4 <- list(
  "CD4 EM",
  "CD4 CM",
  "CD4 Naive",
  "CD4 Treg"
)
label_b <- list("Naive B cells", "Class Switch IgD")
label_tcrgd <- list("TCRgd DP", "TCRgd1", "TCRgd2", "TCRgd3")
label_treg <- list("Treg Memory Activated")

fun_label_cleanup <- function(label, prefix = "") {
  if(grepl("Parent", label)) {
    split_label <- str_split(prefix, " ")[[1]]
    label <- case_when(
      paste(split_label[1:2], collapse = " ") %in% label_cd8 ~ str_replace(label, "Parent", "CD8"),
      paste(split_label[1:2], collapse = " ") %in% label_cd4 ~ str_replace(label, "Parent", "CD4"),
      paste(split_label[1:3], collapse = " ") %in% label_b ~ str_replace(label, "Parent", "B"),
      split_label[1] %in% label_tcrgd ~ str_replace(label, "Parent", "TCRgd"),
      paste(split_label[1:2], collapse = " ") %in% label_tcrgd ~ str_replace(label, "Parent", "TCRgd"),
      paste(split_label[1:3], collapse = " ") %in% label_treg ~ str_replace(label, "Parent", "Treg"),
      TRUE ~ label
    )
  }
  str_replace_all(label, "TCRgd", "TCR\u03B3\u03B4") %>%
    str_replace("Switch ", "Switched ") %>%
    str_replace(" neg", "-") %>%
    str_replace(" pos", "+") %>%
    return()
}
# Function to generating a Y axis label using the variable name
fun_flow_y_label <- function(flow) {
  label <- str_split(flow, " \\| ")[[1]][2]
  prefix <- str_replace_all(str_split(flow, " \\| ")[[1]][1], "\\.", " ")
  label <- case_when(
      grepl("Freq", label) ~ paste0("% of ", str_split(str_replace(label, "Freq. of ", ""), "\\.")[[1]][1], " Cells"),
      grepl("Median", label) ~ paste0(str_replace(str_replace(label, "Median \\(", ""), "\\)", ""), " MFI"),
      TRUE ~ label
    )
  label %>%
    fun_label_cleanup(prefix) %>%
    return()
}


# Function to generating a title using the variable name
fun_flow_title <- function(flow) {
  label <- str_replace_all(str_split(flow, " \\| ")[[1]][1], "\\.", " ")
  label %>%
    fun_label_cleanup() %>%
    return()
}

# Saves all 5 plots as images
fun_flow_svg <- function(flow) {
  str_name <- flow %>%
    tolower() %>%
    str_replace_all("\\. ", "-") %>%
    str_replace_all("\\| ", "") %>%
    str_replace_all(" ", "-") %>%
    str_replace_all("\\.", "-") %>%
    str_replace_all("\\(", "") %>%
    str_replace_all("\\)", "")

  plot_nsl <- fun_plot_facet_box(flow, fun_flow_y_label(flow), fun_flow_title(flow), TRUE, fun = "mean")
  if(nrow(plot_nsl[[1]]$data) == 0) {
    plot_nsl[[1]] <- ggplot(data = data.frame()) + geom_blank()
  }
  plot_ns <- fun_plot_facet_box(flow, fun_flow_y_label(flow), fun_flow_title(flow), FALSE, fun = "mean")
  if(nrow(plot_ns[[1]]$data) == 0) {
    plot_ns[[1]] <- ggplot(data = data.frame()) + geom_blank()
  }
  ggsave(paste0(STR_PLOT_DIR_FLOW, str_name, "-box.svg"), plot_ns[[1]], width = INT_FIG_WIDTH, height = INT_FIG_HEIGHT)
  ggsave(paste0(STR_PLOT_DIR_FLOW, str_name, "-box-log.svg"), plot_nsl[[1]], width = INT_FIG_WIDTH, height = INT_FIG_HEIGHT)
  return(list(plot_ns[[1]], plot_nsl[[1]], plot_ns[[2]]))
}

# Saves all plots
list_plots <- lapply(list_flow_names, fun_flow_svg)

tib_ns <- bind_rows(lapply(list_plots, get_lists, 3))

list_plots_log <- lapply(list_plots, get_lists, 2)
list_plots <- lapply(list_plots, get_lists, 1)
names(list_plots_log) <- list_flow_names
names(list_plots) <- list_flow_names
saveRDS(list_plots_log, paste0(STR_PLOT_DIR_FLOW, "flow_plots_log.rds"))
saveRDS(list_plots, paste0(STR_PLOT_DIR_FLOW, "flow_plots.rds"))
writexl::write_xlsx(tib_ns, paste0(STR_PLOT_DIR_FLOW, "flow_ns.xlsx"))

# Exporting all flow data
tib_flow_all %>%
  writexl::write_xlsx(paste0(STR_DATA_DIR_FLOW, "flow-all.xlsx"))

```

```{r ELISA - Plotting}
# Including same samples used for flow, removing samples without a day (healthy donors)
tib_elisa_analysis <- tib_elisa_raw %>%
  left_join(tib_patients_all %>% select(id, age_d0, convrecip, convrecipdate, Remdesivir, Tocilizumab,
                                        healthy, basic_include, sex, sfseverity_highest, sfratio_lowest), by = c("id")) %>%
  # Getting day of measurement, binning into groups
  mutate(
    ig = factor(ig),
    sr = factor(sr),
    date = as_date(date),
    day = as.integer(date - d0),
    convrecipdate = as_date(convrecipdate),
    dayconv = as.integer(convrecipdate - d0),
    recoverygroup = cut(day, c(-1, 9, 19, 59, 120, Inf), c("Days 0-9", "Days 10-19", "Days 20-59", "Days 60-120", "Days >120")),
    thirtydaygroup = cut(day, c(-1, 30, Inf), c("Days 0-30", "Days >30")),
    titerseveritygroup = cut(day, c(-1, 9, 30, Inf), c("Days 0-9", "Days 10-30", "Days >31")),
    agegroup = cut(age_d0, c(-1, 50, 60, 70, Inf), c("<50", "50s", "60s", ">70")),
    rmdstoci = factor(case_when(
      Remdesivir & Tocilizumab ~ "Remdesivir & Tocilizumab",
      Remdesivir ~ "Remdesivir",
      Tocilizumab ~ "Tocilizumab",
      TRUE ~ "Neither"
    ), levels = c("Remdesivir & Tocilizumab", "Remdesivir", "Tocilizumab", "Neither"))
  ) %>%
  filter(
    basic_include,
    !healthy
  )

# Removing convalescent plasma
tib_elisa_include_noconv <- tib_elisa_analysis %>%
  filter(
    !convrecip
  )


########################
#       PLOTTING       #
########################

# 
# 
# Patient groups: Main flow cohort minus convalescent plasma recipients for most graphs
# 
# A Shape of all Total Ig over time 
# A: Spike and RBD titer (total Ig) vs DPSO.  No preference on how to color lines. I think it’s fine with them each in black.  All data points available per patient through D30
list_ns <- list()

tib_igt_time <- tib_elisa_include_noconv %>%
  filter(
    ig == "Total Ig",
    thirtydaygroup == "Days 0-30"
  ) %>%
  group_by(sr, id, day, rmdstoci, sfseverity_highest) %>%
  summarise(maxig = max(value))

plot_igt_time <- tib_igt_time %>%
  ggplot(aes(x = day, y = maxig, group = id, color = sfseverity_highest)) +
      theme_bw() +
    geom_point() +
    geom_line() +
    geom_hline(aes(yintercept = 50), linetype = "dashed", color = "grey", size = 1) +
    scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) +
    annotation_logticks(sides = "l") +
    scale_colour_manual(values = plotcolors()) +
    ylab("Titer") + xlab("DPSO") +
    facet_wrap(~sr) + 
    theme(strip.text.x = element_text(size = INT_SIG_SIZE*4),
          axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5)) +
    guides(color = FALSE)
#print(plot_igt_time)

list_ns["Total Ig by Time"] <- tib_igt_time %>%
  group_by(sr) %>%
  select(sr, id) %>%
  unique() %>%
  summarise(n = n()) %>%
  list()

# B IgG and IgM over time
# B: Spike and RBD IgG and IgM vs time range.  Let’s use the same dot + boxplots that Jovian is using for cytokine data. Data to include: peak titer reached during each time phase per patient (one dot per timepoint per patient).  Time ranges: Acute infection (D10-19), recovery (D20-59), late recovery (D60 – 120).  
iggm_time_groups <- c("Days 10-19", "Days 20-59", "Days 60-120")

tib_iggm_time <- tib_elisa_include_noconv %>%
  filter(
    ig != "Total Ig",
    recoverygroup %in% iggm_time_groups
  ) %>%
  group_by(sr, recoverygroup, ig, id, sfseverity_highest) %>%
  summarise(maxig = max(value))

list_ns["IgG-IgM by Time"] <- tib_iggm_time %>%
  ungroup() %>%
  group_by(ig, sr, recoverygroup) %>%
  select(ig, sr, recoverygroup, id) %>%
  unique() %>%
  summarise(n = n()) %>%
  list()

list_ns["IgG-IgM by Time with Severity"] <- tib_iggm_time %>%
  ungroup() %>%
  group_by(ig, sr, recoverygroup, sfseverity_highest) %>%
  select(ig, sr, recoverygroup, sfseverity_highest, id) %>%
  unique() %>%
  summarise(n = n()) %>%
  list()

# p-value comparison pairings
comparisons_1 <- list(
  c(iggm_time_groups[1], iggm_time_groups[2]),
  c(iggm_time_groups[2], iggm_time_groups[3])
)

comparisons_2 <- list(
  c(iggm_time_groups[1], iggm_time_groups[3])
)


plot_iggm_time_box <- tib_iggm_time %>%
  ggplot(aes(x = recoverygroup, y = maxig, color = ig)) +
      theme_bw() +
  # Box plot with jitter
  geom_boxplot(outlier.shape = NA) +
  geom_point(position=position_jitterdodge(), aes(color = ig), size = INT_SIG_SIZE) +
  # Labels
  labs(color = "") + ylab("Titer") + #guides(color = FALSE) + 
#  scale_colour_manual(values = rev(LIST_PLOT_COLORS)) +
  # Somewhat hacky way of showing N for each group at the time at -5% of the max value to ensure it shows up on the plot
#  geom_text(data = tib_plot_n, aes(x = sfseverity_highest, y = pos, label = ns), colour="grey20", size=3) +
  # Remove ticks and variable labels
  geom_hline(aes(yintercept = 50), linetype = "dashed", color = "grey", size = 1) +
  geom_signif(aes(x = recoverygroup, y = maxig, color = recoverygroup), comparisons = comparisons_1, color = "black", map_signif_level = fun_significance, margin_top = 0.05) +
  geom_signif(aes(x = recoverygroup, y = maxig, color = recoverygroup), comparisons = comparisons_2, color = "black", map_signif_level = fun_significance, margin_top = 0.15) +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "l") +
  theme(axis.title.x=element_blank(), axis.ticks.x = element_blank(),
          axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5)) + 
  facet_wrap(~sr) + 
    theme(strip.text.x = element_text(size = INT_SIG_SIZE*4))
plot_igm_time_box <- tib_iggm_time %>%
  filter(ig == "IgM") %>%
  ggplot(aes(x = recoverygroup, y = maxig)) +
      theme_bw() +
  # Box plot with jitter
  geom_boxplot(outlier.shape = NA) +
  # Labels
  labs(color = "") + ylab("Titer") + #guides(color = FALSE) + 
#  scale_colour_manual(values = rev(LIST_PLOT_COLORS)) +
  # Somewhat hacky way of showing N for each group at the time at -5% of the max value to ensure it shows up on the plot
#  geom_text(data = tib_plot_n, aes(x = sfseverity_highest, y = pos, label = ns), colour="grey20", size=3) +
  # Remove ticks and variable labels
  geom_hline(aes(yintercept = 50), linetype = "dashed", color = "grey", size = 1) +
  geom_signif(aes(x = recoverygroup, y = maxig, color = recoverygroup), comparisons = comparisons_1, color = "black", map_signif_level = fun_significance, margin_top = 0.05) +
  geom_signif(aes(x = recoverygroup, y = maxig, color = recoverygroup), comparisons = comparisons_2, color = "black", map_signif_level = fun_significance, margin_top = 0.15) +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "l") +
  theme(axis.title.x=element_blank(), axis.ticks.x = element_blank(),
          axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5)) + 
  facet_wrap(~sr) + 
    theme(strip.text.x = element_text(size = INT_SIG_SIZE*4)) +
  ggtitle("IgM")
plot_igg_time_box <- tib_iggm_time %>%
  filter(ig == "IgG") %>%
  ggplot(aes(x = recoverygroup, y = maxig)) +
      theme_bw() +
  # Box plot with jitter
  geom_boxplot(outlier.shape = NA) +
  # Labels
  labs(color = "") + ylab("Titer") + #guides(color = FALSE) + 
#  scale_colour_manual(values = rev(LIST_PLOT_COLORS)) +
  # Somewhat hacky way of showing N for each group at the time at -5% of the max value to ensure it shows up on the plot
#  geom_text(data = tib_plot_n, aes(x = sfseverity_highest, y = pos, label = ns), colour="grey20", size=3) +
  # Remove ticks and variable labels
  geom_hline(aes(yintercept = 50), linetype = "dashed", color = "grey", size = 1) +
  geom_signif(aes(x = recoverygroup, y = maxig, color = recoverygroup), comparisons = comparisons_1, color = "black", map_signif_level = fun_significance, margin_top = 0.05) +
  geom_signif(aes(x = recoverygroup, y = maxig, color = recoverygroup), comparisons = comparisons_2, color = "black", map_signif_level = fun_significance, margin_top = 0.15) +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "l") +
  theme(axis.title.x=element_blank(), axis.ticks.x = element_blank(),
          axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5)) + 
  facet_wrap(~sr) + 
    theme(strip.text.x = element_text(size = INT_SIG_SIZE*4)) +
  ggtitle("IgG")
#print(plot_iggm_time_box)



# plot_iggm_time_scatter <- tib_iggm_time %>%
#   ggplot(aes(x = day, y = maxig, color = ig)) +
#   # Box plot with jitter
#   geom_point() +
#   # Labels
#   labs(fill = "Immunoglobulin") + ylab("Titer") + guides(color = FALSE) + 
# #  scale_colour_manual(values = rev(LIST_PLOT_COLORS)) +
#   # Somewhat hacky way of showing N for each group at the time at -5% of the max value to ensure it shows up on the plot
# #  geom_text(data = tib_plot_n, aes(x = sfseverity_highest, y = pos, label = ns), colour="grey20", size=3) +
#   # Remove ticks and variable labels
#   scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
#                 labels = trans_format("log10", math_format(10^.x))) +
#   theme(axis.title.x=element_blank(), axis.ticks.x = element_blank()) + 
#   facet_wrap(~sr)
# print(plot_iggm_time_scatter)

# C Total Ig with Disease severity
# C: Spike and RBD titer (total Ig, max titer in the appropriate time range) vs max severity for the hospitalization (SF).  Can you try filtering this for D10-21 and then also try D15-21, and see how many points the narrower time range excludes?  One dot per patient representing the max titer reached during that time range. 
    # testgroup1 = cut(day, c(-1, 9, 30, Inf), c("Days 0-9", "Days 10-30", "Days >21")),
    # testgroup2 = cut(day, c(-1, 14, 21, Inf), c("Days 0-14", "Days 15-21", "Days >21")),
tib_igt_sf <- tib_elisa_include_noconv %>%
  filter(
    ig == "Total Ig",
    titerseveritygroup == "Days 10-30"
  ) %>%
  group_by(sr, id, sfratio_lowest) %>%
  summarise(maxig = max(value))

formula <- y ~ poly(x,1)

plot_igt_sf <- tib_igt_sf %>%
  ggplot(aes(x = sfratio_lowest, y = maxig)) +
      theme_bw() +
  geom_point(size = INT_SIG_SIZE) +
  ylab("Titer") + xlab("Max Severity Reached (S/F Ratio)") + 
  geom_smooth(method = "glm", formula = formula,
                    method.args = list(family = gaussian(link = 'log'))) +
  # Adding CI
  stat_poly_eq(
    aes(label = paste(stat(p.value.label), stat(rr.label), sep = "*\", \"*")),
    formula = formula,
    label.x = "right", label.y = "bottom", size = 3,
    parse = TRUE
    ) +
  geom_hline(aes(yintercept = 50), linetype = "dashed", color = "grey", size = 1) +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "l") +
  facet_wrap(~sr)+
theme(strip.text.x = element_text(size = INT_SIG_SIZE*4), axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5))
#print(plot_igt_sf)

list_ns["Total Ig by Max Severity"] <- tib_igt_sf %>%
  ungroup() %>%
  group_by(sr) %>%
  select(sr, id) %>%
  unique() %>%
  summarise(n = n()) %>%
  list()

# D Total Ig with Age, (Gender – supplemental)
# D: Spike and RBD total IgG titer (max reached D0-30) versus age – boxplots in buckets.  Also look at as a dotpot correlation with age as a continuous variable?  
tib_igt_age <- tib_elisa_include_noconv %>%
  filter(
    ig == "Total Ig",
    titerseveritygroup == "Days 10-30"
  ) %>%
  group_by(sr, agegroup, id, age_d0, sfseverity_highest) %>%
  summarise(maxig = max(value))

list_ns["Total Ig by Age"] <- tib_igt_age %>%
  ungroup() %>%
  group_by(sr, agegroup) %>%
  select(sr, agegroup, id) %>%
  summarise(n = n()) %>%
  list()

plot_igt_age_box <- tib_igt_age %>%
  ggplot(aes(x = agegroup, y = maxig, color = agegroup)) +
      theme_bw() +
  # Box plot with jitter
  geom_boxplot(outlier.shape = NA) +
  geom_point(position=position_jitterdodge(), size = INT_SIG_SIZE) +
  # Labels
  ylab("Titer") + guides(color = FALSE) + 
#  scale_colour_manual(values = rev(LIST_PLOT_COLORS)) +
  # Somewhat hacky way of showing N for each group at the time at -5% of the max value to ensure it shows up on the plot
#  geom_text(data = tib_plot_n, aes(x = sfseverity_highest, y = pos, label = ns), colour="grey20", size=3) +
  # Remove ticks and variable labels
  geom_hline(aes(yintercept = 50), linetype = "dashed", color = "grey", size = 1) +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "l") +
  theme(axis.title.x=element_blank(), axis.ticks.x = element_blank()) + 
  facet_wrap(~sr)+
theme(strip.text.x = element_text(size = INT_SIG_SIZE*4), axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5))
#print(plot_igt_age_box)

plot_igt_age_scatter <- tib_igt_age %>%
  ggplot(aes(x = age_d0, y = maxig, color = sfseverity_highest)) +
  theme_bw() +
  # Box plot with jitter
  geom_point() +
  # Labels
  guides(color = FALSE) + ylab("Titer") +
  geom_hline(aes(yintercept = 50), linetype = "dashed", color = "grey", size = 1) +
  scale_colour_manual(values = plotcolors(rev = TRUE, int_n = 3)) +
  # Somewhat hacky way of showing N for each group at the time at -5% of the max value to ensure it shows up on the plot
#  geom_text(data = tib_plot_n, aes(x = sfseverity_highest, y = pos, label = ns), colour="grey20", size=3) +
  # Remove ticks and variable labels
  geom_smooth(aes(x = age_d0, y = maxig, color = NA), color = "blue", method = "lm", formula = y ~ poly(x, 1)) +#,
#                      method.args = list(family = gaussian(link = 'log'))) } +
    # Adding CI
  stat_poly_eq(
    aes(color = NA, label = paste(stat(p.value.label), stat(rr.label), sep = "*\", \"*")),
    formula = y ~ poly(x, 1),
    label.x = "right", label.y = "bottom", size = 3,
    parse = TRUE
  ) +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  theme(axis.title.x=element_blank(), axis.ticks.x = element_blank()) +
  facet_wrap(~sr)
# print(plot_igt_age_scatter)

tib_igt_sex <- tib_elisa_include_noconv %>%
  filter(
    ig == "Total Ig",
    titerseveritygroup == "Days 10-30"
  ) %>%
  group_by(sr, sex, id, age_d0) %>%
  summarise(maxig = max(value))

list_ns["Total Ig by Sex"] <- tib_igt_sex %>%
  ungroup() %>%
  group_by(sr, sex) %>%
  select(sr, sex, id) %>%
  unique() %>%
  summarise(n = n()) %>%
  list()

comparisons_1 <- list(
  c("M", "F")
)

plot_igt_sex_box <- tib_igt_sex %>%
  ggplot(aes(x = sex, y = maxig, color = sex)) +
      theme_bw() +
  # Box plot with jitter
  geom_boxplot(outlier.shape = NA) +
  geom_point(position=position_jitterdodge(), size = INT_SIG_SIZE) +
  # Labels
  geom_hline(aes(yintercept = 50), linetype = "dashed", color = "grey", size = 1) +
  geom_signif(aes(x = sex, y = maxig, color = sex), comparisons = comparisons_1, color = "black", map_signif_level = fun_significance, margin_top = 0.05) +
  ylab("Titer") + guides(color = FALSE) + 
#  scale_colour_manual(values = rev(LIST_PLOT_COLORS)) +
  # Somewhat hacky way of showing N for each group at the time at -5% of the max value to ensure it shows up on the plot
#  geom_text(data = tib_plot_n, aes(x = sfseverity_highest, y = pos, label = ns), colour="grey20", size=3) +
  # Remove ticks and variable labels
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "l") +
  theme(axis.title.x=element_blank(), axis.ticks.x = element_blank()) + 
  facet_wrap(~sr)+
theme(strip.text.x = element_text(size = INT_SIG_SIZE*4), axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5))
#print(plot_igt_sex_box)


# E Total Ig with RMDS, Toci
# E: Spike and RBD total IgG titer vs DPSO, divided by COVID treatment.  Treatment groups: RMDS, tocilizumab (combine on and off study), steroids (during COVID admission), none of the above 3.  Calculate time to peak titer and slope of individual patient lines titer rise (see Emily code)
plot_igt_time_rmdstoci <- tib_igt_time %>%
  ggplot(aes(x = day, y = maxig, group = id, color = rmdstoci)) +
    theme_bw() +
    geom_point() +
    geom_line() +
    scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) +
    annotation_logticks(sides = "l") +
    geom_hline(aes(yintercept = 50), linetype = "dashed", color = "grey", size = 1) +
    scale_colour_manual(values = rev(c("black", hcl(h = seq(15, 375, length = 4), l = 65, c = 100)[2:3]))) +
    ylab("Titer") + xlab("DPSO") + labs(color = "Treatment") +
    facet_wrap(~sr)+
theme(strip.text.x = element_text(size = INT_SIG_SIZE*4), axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5))


# p-value comparison pairings
comparisons_1 <- list(
  c("Remdesivir", "Tocilizumab"),
  c("Tocilizumab", "Neither")
)

comparisons_2 <- list(
  c("Remdesivir", "Neither")
)

plot_igt_time_rmdstoci_box <- tib_igt_time %>%
  group_by(sr, id, rmdstoci) %>%
  summarise(maxig = max(maxig, na.rm = TRUE)) %>%
  ggplot(aes(x = rmdstoci, y = maxig, color = rmdstoci)) +
    theme_bw() +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position=position_jitterdodge(), size = INT_SIG_SIZE) +
    geom_signif(comparisons = comparisons_1, color = "black", map_signif_level = fun_significance, margin_top = 0.05) +
    geom_signif(comparisons = comparisons_2, color = "black", map_signif_level = fun_significance, margin_top = 0.15) +
    scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) +
    annotation_logticks(sides = "l") +
    geom_hline(aes(yintercept = 50), linetype = "dashed", color = "grey", size = 1) +
    scale_colour_manual(values = rev(c("black", hcl(h = seq(15, 375, length = 4), l = 65, c = 100)[2:3]))) +
    ylab("Titer") + xlab("DPSO") + labs(color = "Treatment") +
    facet_wrap(~sr)+
theme(strip.text.x = element_text(size = INT_SIG_SIZE*4), axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5))
#print(plot_igt_time_rmdstoci)

list_ns["Total Ig by RMDS-Toci"] <- tib_igt_time %>%
  ungroup() %>%
  group_by(sr, rmdstoci) %>%
  select(sr, id, rmdstoci) %>%
  unique() %>%
  summarise(n = n()) %>%
  list()

tib_elisa_include_conv <- tib_elisa_analysis %>%
  filter(convrecip) %>%
  mutate(
    dayconv0 = day - dayconv,
    prepostconv = cut(dayconv0, c(-Inf,0,Inf),c("Pre-Infusion", "Post-Infusion"))
  )
  
tib_igt_prepostconv <- tib_elisa_include_conv %>%
  filter(convrecip) %>%
  filter(
    ig == "Total Ig"
  ) %>%
  group_by(sr, prepostconv, id, dayconv0) %>%
  summarise(maxig = max(value))

plot_igt_prepostconv_box <- tib_igt_prepostconv %>%
  ggplot(aes(x = prepostconv, y = maxig, fill = prepostconv)) +
      theme_bw() +
  # Box plot with jitter
  geom_boxplot(outlier.shape = NA) +
  geom_point(position=position_jitterdodge(), size = INT_SIG_SIZE) +
  # Labels
  labs(fill = "Convalescent Plasma") + ylab("Titer") +
#  scale_colour_manual(values = rev(list_plot_colors)) +
  # Somewhat hacky way of showing N for each group at the time at -5% of the max value to ensure it shows up on the plot
#  geom_text(data = tib_plot_n, aes(x = sfseverity_highest, y = pos, label = ns), colour="grey20", size=3) +
  # Remove ticks and variable labels
  geom_hline(aes(yintercept = 50), linetype = "dashed", color = "grey", size = 1) +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "l") +
  theme(axis.title.x=element_blank(), axis.ticks.x = element_blank()) + 
  facet_wrap(~sr)+
theme(strip.text.x = element_text(size = INT_SIG_SIZE*4), axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5))
#print(plot_igt_prepostconv_box)

plot_igt_prepostconv_scatter <- tib_igt_prepostconv %>%
  ggplot(aes(x = dayconv0, y = maxig, color = prepostconv, group = id)) +
      theme_bw() +
  # Box plot with jitter
  geom_point(size = INT_SIG_SIZE) +
  geom_line() +
  # Labels
  labs(color = "Convalescent Plasma") + ylab("Titer") +
#  scale_colour_manual(values = rev(list_plot_colors)) +
  # Somewhat hacky way of showing N for each group at the time at -5% of the max value to ensure it shows up on the plot
#  geom_text(data = tib_plot_n, aes(x = sfseverity_highest, y = pos, label = ns), colour="grey20", size=3) +
  # Remove ticks and variable labels
  geom_hline(aes(yintercept = 50), linetype = "dashed", color = "grey", size = 1) +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "l") +
  theme(axis.title.x=element_blank(), axis.ticks.x = element_blank()) + 
  facet_wrap(~sr)+
theme(strip.text.x = element_text(size = INT_SIG_SIZE*4), axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5))
#print(plot_igt_prepostconv_scatter)


list_plots <- list(
  "plot_igt_time",
  "plot_iggm_time_box",
#  "plot_iggm_time_scatter",
  "plot_igt_sf",
  "plot_igt_age_box",
  "plot_igt_age_scatter",
  "plot_igt_sex_box",
  "plot_igt_time_rmdstoci",
  "plot_igt_time_rmdstoci_box",
  "plot_igt_prepostconv_box",
  "plot_igt_prepostconv_scatter"
)

fun_elisa_svg <- function(str_plot) {
  ggsave(paste0(STR_PLOT_DIR_ELISA, str_remove(string = str_plot, pattern = "plot_"), ".svg"),
    get(str_plot), width = INT_FIG_WIDTH*2, height = INT_FIG_HEIGHT)
}

lapply(list_plots, fun_elisa_svg)

list_ggplots <- lapply(list_plots, get)
names(list_ggplots) <- list_plots

saveRDS(list_ggplots, paste0(STR_PLOT_DIR_ELISA, "elisa.rds"))

list_ns %>%
  writexl::write_xlsx(paste0(STR_PLOT_DIR_ELISA, "elisa_ns.xlsx"))

tib_elisa_raw %>%
  writexl::write_xlsx(paste0(STR_DATA_DIR_ELISA, "elisa_all.xlsx"))

```

```{r Miscellaneous - Plotting - Data Processing}

tib_data_all_analysis <- tib_data_include %>%
  group_by(id) %>%
  filter(!healthy) %>%
  mutate(
    sfseverity_highest = as.character(sfseverity_highest),
    elispot_s_m_n = ifelse((day >= 21) | (day <= -1), NA_real_, elispot_s_m_n),
    nlratio = as.double(`Absolute neutrophils`)/as.double(`Absolute lymphocytes`)
  ) %>%
  arrange(day) %>%
  summarise(
    sfseverity_highest = as.character(first(sfseverity_highest)),
    healthy = first(healthy),
    `Max Ferritin` = max(Ferritin, na.rm = TRUE),
    `Max CRP` = max(CRP, na.rm = TRUE),
    `Max D-Dimer` = max(`D-dimer`, na.rm = TRUE),
    `WBC Nadir` = min(WBC, na.rm = TRUE),
    `Lymphocyte Nadir` = min(`Absolute lymphocytes`, na.rm = TRUE),
    `Monocyte Nadir` = min(`Absolute Monocytes`, na.rm = TRUE),
    `Viral Load` = max(ddpcr_n, na.rm = TRUE),
    `IFNg ELISPOT` = mean(elispot_s_m_n, na.rm = TRUE),
    `Neutrophil/Lymphocyte Ratio` = first(na.omit(nlratio)),
    `Vitamin D2` = first(na.omit(`Vitamin D2`)),
    `Vitamin D3` = first(na.omit(`Vitamin D3`))
  ) %>%
  mutate(
    across(everything(), ~ifelse(is.infinite(.), NA, .)),
    across(everything(), ~ifelse(is.nan(.), NA, .)),
    sfseverity_highest = factor(as.character(sfseverity_highest), levels = sflevels(rev = TRUE, healthy = FALSE))
  )

tib_data_other <- tib_data_include

for (var in tib_columns$variable) {
  if (var %in% colnames(tib_data_other)) {
    tib_data_other <- tib_data_other %>%
      rename(
        !!as.symbol(tib_columns$name[tib_columns$variable == var]) := !!as.symbol(var)
      )
  }
}

list_cytokines_all <- str_replace(list_cytokines_all, "/Rantes", "")

get_lists <- function(list_stuff, index) {
  return(list_stuff[[index]])
}


```

```{r Miscellaneous - Plotting - Double Box Plots}

tib_doublebox <- tib_data_include %>%
  mutate(
    sfseverity_highest = factor(case_when(
      healthy ~ "Healthy",
      TRUE ~ as.character(sfseverity_highest)), levels = sflevels(TRUE,TRUE)),
    tg = cut(day, c(-1, 9, 30, Inf), c("Days 0-9", "Days 10-30", NA)),
    `CD4/CD8 Ratio` = `CD4 | Freq. of Parent` / `CD8 | Freq. of Parent`,
    `Neutrophil/Lymphocyte Ratio` = `Absolute neutrophils` / `Absolute lymphocytes`) %>%
  group_by(id, tg, sfseverity_highest) %>%
  summarise(
    `CD4/CD8 Ratio` = max(`CD4/CD8 Ratio`, na.rm = TRUE),
    `Neutrophil/Lymphocyte Ratio` = max(`Neutrophil/Lymphocyte Ratio`, na.rm = TRUE))

plot_double_box <- function(name, healthy = FALSE, logscale = FALSE) {
  # p-value comparison pairings
  tib_data <- tib_doublebox %>%
    filter(across(all_of(name), ~(!is.infinite(.))))
  if (healthy) {
    tib_data <- tib_data %>%
      filter(tg %in% c("Days 0-9", "Days 10-30")) %>%
      bind_rows(tib_data %>%
                  filter(sfseverity_highest == "Healthy") %>%
                  mutate(tg = "Days 0-9")) %>%
      bind_rows(tib_data %>%
                  filter(sfseverity_highest == "Healthy") %>%
                  mutate(tg = "Days 10-30"))
    comparisons_1 <- list(
      c(sflevels(TRUE, TRUE)[1], sflevels(TRUE, TRUE)[2]),
      c(sflevels(TRUE, TRUE)[2], sflevels(TRUE, TRUE)[3]),
      c(sflevels(TRUE, TRUE)[3], sflevels(TRUE, TRUE)[4])
    )

    comparisons_2 <- list(
      c(sflevels(TRUE, TRUE)[1], sflevels(TRUE, TRUE)[3])
    )

    comparisons_3 <- list(
      c(sflevels(TRUE, TRUE)[2], sflevels(TRUE, TRUE)[4])
    )

    comparisons_4 <- list(
      c(sflevels(TRUE, TRUE)[1], sflevels(TRUE, TRUE)[4])
    )
  } else {
    comparisons_1 <- list(
      c(sflevels()[1], sflevels()[2]),
      c(sflevels()[2], sflevels()[3])
    )
    
    comparisons_2 <- list(
      c(sflevels()[1], sflevels()[3])
    )
    tib_data <- tib_data %>%
      filter(tg %in% c("Days 0-9", "Days 10-30"))
  }
  
  list_ns <- tib_data %>%
    group_by(tg, sfseverity_highest) %>%
    select(id, tg, sfseverity_highest) %>%
    unique() %>%
    summarise(n = n()) %>%
    list()
  
  plot_double <- tib_data %>%
    ggplot(aes_string(x = "sfseverity_highest", y = paste0("`",name, "`"), color = "sfseverity_highest")) +
      theme_bw() +
      # Box plot with jitter
      geom_boxplot(outlier.shape = NA) +
      geom_point(position=position_jitterdodge(), size = INT_SIG_SIZE) +
      # Labels
      ggtitle(name) + guides(color = FALSE) + 
      {if (healthy) scale_colour_manual(values = plotcolors(TRUE, int_n = 4))} +
      {if (!healthy) scale_colour_manual(values = plotcolors(TRUE, int_n = 3))} +
    # Somewhat hacky way of showing N for each group at the time at -5% of the max value to ensure it shows up on the plot
    #  geom_text(data = tib_plot_n, aes(x = sfseverity_highest, y = pos, label = ns), colour="grey20", size=3) +
    # Remove ticks and variable labels
      {if (healthy) geom_signif(aes_string(x = "sfseverity_highest", y = paste0("`",name, "`"), color = "sfseverity_highest"), comparisons = comparisons_1, color = "black", map_signif_level = fun_significance, margin_top = 0.05, textsize = INT_SIG_SIZE)} +
      {if (healthy) geom_signif(aes_string(x = "sfseverity_highest", y = paste0("`",name, "`"), color = "sfseverity_highest"), comparisons = comparisons_2, color = "black", map_signif_level = fun_significance, margin_top = 0.15, textsize = INT_SIG_SIZE)} +
      {if (healthy) geom_signif(aes_string(x = "sfseverity_highest", y = paste0("`",name, "`"), color = "sfseverity_highest"), comparisons = comparisons_3, color = "black", map_signif_level = fun_significance, margin_top = 0.25, textsize = INT_SIG_SIZE)} +
      {if (healthy) geom_signif(aes_string(x = "sfseverity_highest", y = paste0("`",name, "`"), color = "sfseverity_highest"), comparisons = comparisons_4, color = "black", map_signif_level = fun_significance, margin_top = 0.35, textsize = INT_SIG_SIZE)} +
      {if (!healthy) geom_signif(aes_string(x = "sfseverity_highest", y = paste0("`",name, "`"), color = "sfseverity_highest"), comparisons = comparisons_1, color = "black", map_signif_level = fun_significance, margin_top = 0.05)} +
      {if (!healthy) geom_signif(aes_string(x = "sfseverity_highest", y = paste0("`",name, "`"), color = "sfseverity_highest"), comparisons = comparisons_2, color = "black", map_signif_level = fun_significance, margin_top = 0.15)} +
      theme(axis.title.x=element_blank(), axis.ticks.x = element_blank(), axis.title.y = element_blank(), axis.text.x = element_blank()) + 
    theme(strip.text.x = element_text(size = INT_SIG_SIZE*4), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5)) +
      {if (logscale) scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) } +
      {if (logscale) annotation_logticks(sides = "l") } +
      facet_wrap(~tg)
  str_name <- name %>%
    tolower() %>%
    str_replace_all("\\. ", "-") %>%
    str_replace_all("\\| ", "") %>%
    str_replace_all(" ", "-") %>%
    str_replace_all("\\/", "-") %>%
    str_replace_all("\\+", "-") %>%
    str_replace_all("\\.", "-") %>%
    str_replace_all("\\(", "") %>%
    str_replace_all("\\)", "")

  plot_double %>%
    ggsave(filename = paste0(STR_PLOT_DIR_OTHER, str_name, "-earlylate", {if(logscale) "-log"}, ".svg"), width = INT_FIG_WIDTH, height = INT_FIG_HEIGHT)
  return(list(plot_double, list_ns))
}

list_doubles <- c("CD4/CD8 Ratio", "CD4/CD8 Ratio", "Neutrophil/Lymphocyte Ratio")
list_healthy <- c(TRUE, TRUE, FALSE)
list_logs <- c(TRUE, FALSE, FALSE)

list_plotns <- mapply(plot_double_box, list_doubles, list_healthy, list_logs, SIMPLIFY = FALSE)

tib_ns <- bind_rows(lapply(list_plotns, get_lists, 2))
list_plots <- lapply(list_plotns, get_lists, 1)
names(list_plots) <- list_doubles

saveRDS(list_plots, paste0(STR_PLOT_DIR_OTHER, "earlylateboxplots.rds"))
writexl::write_xlsx(tib_ns, paste0(STR_PLOT_DIR_OTHER, "earlylateboxplot_ns.xlsx"))

```

```{r Miscellaneous - Plotting - Single Box Plots}

fun_boxit <- function(data, title, logscale, nrange){
  fun_cytokine_title <- function(label) {
    label %>% str_replace("IFNa", "IFN\u03B1") %>%
      str_replace("IFNg", "IFN\u03B3") %>%
      str_replace("(Fa)$", "F\u03B1") %>%
      str_replace("(Ra)$", "R\u03B1") %>%
      str_replace("1a", "1\u03B1") %>%
      str_replace("1b", "1\u03B2") %>%
    return()
  }
  
  # p-value comparison pairings
  comparisons_1 <- list(
    c(sflevels()[1], sflevels()[2]),
    c(sflevels()[2], sflevels()[3])
  )

  comparisons_2 <- list(
    c(sflevels()[1], sflevels()[3])
  )

  tib_ns <- data %>%
    group_by(sfseverity_highest) %>%
    select(sfseverity_highest, id) %>%
    unique() %>%
    summarise(ns = n()) %>%
    spread(sfseverity_highest, ns) %>%
    mutate(Study = title) %>%
    relocate(Study)

  plot_one <- data %>%
    ggplot(aes_string(x = "sfseverity_highest", y = paste0("`", title, "`"), color = "sfseverity_highest")) +
    theme_bw() +
    # Box plot with jitter
    annotate("rect", ymin=nrange[1], ymax=nrange[2],
                  xmin=-Inf, xmax=Inf, alpha = 0.3)+
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(width = 0.1, size = INT_SIG_SIZE) +
    # p-values from above
    geom_signif(aes_string(x = "sfseverity_highest", y = paste0("`", title, "`"), color = "sfseverity_highest"), comparisons = comparisons_1, color = "black", map_signif_level = fun_significance, margin_top = 0.05) +
    geom_signif(aes_string(x = "sfseverity_highest", y = paste0("`", title, "`"), color = "sfseverity_highest"), comparisons = comparisons_2, color = "black", map_signif_level = fun_significance, margin_top = 0.15) +
    # Labels
    labs(color = "Severity", title = fun_cytokine_title(title)) + 
    # Colors
    scale_colour_manual(values = plotcolors(rev = TRUE, int_n = 3)) +
    # Legend colors
    #guides(color = guide_legend(reverse = TRUE)) +
    guides(color = FALSE) +
    # Somewhat hacky way of showing N for each group at the time at -3% of the max value to ensure it shows up on the plot
    # Remove ticks and variable labels
    theme(axis.title.x=element_blank(), axis.title.y=element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(),
            axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5)) + 
    {if (logscale) scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
            labels = trans_format("log10", math_format(10^.x))) } +
    {if (logscale) annotation_logticks(sides = "l") }
  return(list(plot_one, tib_ns))
}

fun_box_clinical <- function(name, logscale = FALSE, nrange = c(-Inf, -Inf)) {
  tib_data <- tib_data_all_analysis %>%
    select(id, sfseverity_highest, all_of(name)) %>%
    filter(
      across(all_of(name), ~(!is.na(.))),
      across(all_of(name), ~(!is.infinite(.)))
    ) %>%
    group_by(sfseverity_highest)
  str_name <- name %>%
    tolower() %>%
    str_replace_all("\\. ", "-") %>%
    str_replace_all("\\| ", "") %>%
    str_replace_all(" ", "-") %>%
    str_replace_all("\\/", "-") %>%
    str_replace_all("\\+", "-") %>%
    str_replace_all("\\.", "-") %>%
    str_replace_all("\\(", "") %>%
    str_replace_all("\\)", "")
  list_plotns <- fun_boxit(tib_data, name, logscale, nrange)
  ggsave(list_plotns[[1]], filename = paste0(STR_PLOT_DIR_OTHER, str_name, ".svg"), width = INT_FIG_WIDTH, height = INT_FIG_HEIGHT)
  return(list_plotns)
}
# Ferritin 10-220
# CRP <5
# Dimer <0.42
# Abs Lymphocyte count 0.9-3.3
# ddPCR <0.1

save_rds_ns <- function(list_plot_ns, str_name, str_dir = STR_PLOT_DIR_OTHER) {
  tib_ns <- bind_rows(lapply(list_plot_ns, get_lists, 2))
  list_plots <- lapply(list_plot_ns, get_lists, 1)
  names(list_plots) <- list_clinical_plots
  
  saveRDS(list_plots, paste0(str_dir, str_name, ".rds"))
  writexl::write_xlsx(tib_ns, paste0(str_dir, str_name, "_ns.xlsx"))
}


list_clinical_plots <- list("Max Ferritin", "Max CRP", "Max D-Dimer", "Lymphocyte Nadir", "Viral Load", "IFNg ELISPOT", "Neutrophil/Lymphocyte Ratio",
                            "Vitamin D2", "Vitamin D3")
list_clinical_plots_log <- list(FALSE, FALSE, FALSE, FALSE, TRUE, FALSE, FALSE, FALSE, FALSE)
list_clinical_plots_ranges <- list(c(10,220), c(0, 5), c(0,0.42), c(0.9, 3.3), c(0, 0.1), c(-Inf, 1), c(-Inf, -Inf), c(-Inf, -Inf), c(-Inf, -Inf))

list_plotns <- mapply(fun_box_clinical,
  list_clinical_plots,
  list_clinical_plots_log,
  list_clinical_plots_ranges,
  SIMPLIFY = FALSE)
tib_ns <- bind_rows(lapply(list_plotns, get_lists, 2))
list_plots <- lapply(list_plotns, get_lists, 1)
names(list_plots) <- list_clinical_plots

saveRDS(list_plots, paste0(STR_PLOT_DIR_OTHER, "boxplots.rds"))
writexl::write_xlsx(tib_ns, paste0(STR_PLOT_DIR_OTHER, "boxplot_ns.xlsx"))

```

```{r Miscellaneous - Plotting - Scatter}

fun_scatterit <- function(data, str_x, str_y, logscale_x = FALSE, logscale_y = FALSE, pow = FALSE){
  fun_cytokine_title <- function(label) {
    label %>% str_replace("IFNa", "IFN\u03B1") %>%
      str_replace("IFNg", "IFN\u03B3") %>%
      str_replace("(Fa)$", "F\u03B1") %>%
      str_replace("(Ra)$", "R\u03B1") %>%
      str_replace("1a", "1\u03B1") %>%
      str_replace("1b", "1\u03B2") %>%
    return()
  }
  
  tib_ns <- data %>%
    group_by(sfseverity_highest) %>%
    select(sfseverity_highest, id) %>%
    unique() %>%
    summarise(ns = n()) %>%
    spread(sfseverity_highest, ns) %>%
    mutate(Study = paste0(fun_cytokine_title(str_x), " vs ", fun_cytokine_title(str_y))) %>%
    relocate(Study)

  plot_one <- data %>%
    ggplot(aes_string(x = paste0("`", str_x, "`"), y = paste0("`", str_y, "`"))) +
    theme_bw() +
    geom_point(aes_string(color = "sfseverity_highest")) +
    # Labels
    labs(title = paste0(fun_cytokine_title(str_x), " vs. ", fun_cytokine_title(str_y))) +
    ylab(fun_cytokine_title(str_y)) +
    xlab(fun_cytokine_title(str_x)) +
    # Colors
    scale_colour_manual(values = plotcolors()) +
    # Legend colors
    #guides(color = guide_legend(reverse = TRUE)) +
    guides(color = FALSE) +
    theme(axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5)) + 
    {if (logscale_x) scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
            labels = trans_format("log10", math_format(10^.x))) } +
    {if (logscale_x) annotation_logticks(sides = "b") } +
    {if (logscale_y) scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
            labels = trans_format("log10", math_format(10^.x))) } +
    {if (logscale_y) annotation_logticks(sides = "l") } +
    # Scatter plot
    {if (pow) geom_smooth(method = "lm", formula = y ~ poly(x, 1))} +#,
#                      method.args = list(family = gaussian(link = 'log'))) } +
    # Adding CI
    {if (pow) stat_poly_eq(
      aes(label = paste(stat(p.value.label), stat(rr.label), sep = "*\", \"*")),
      formula = y ~ poly(x, 1),
      label.x = "right", label.y = "bottom", size = 3,
      parse = TRUE
      ) }
  return(list(plot_one, tib_ns))
}

fun_prepscatter <- function(var_x, var_y, fun_x, fun_y, log_x, log_y, pow = FALSE,
                            mindx = -1, maxdx = 300, mindy = -1, maxdy = 300,
                            data = tib_data_other) {
  list_funs <- list(
    max = ~max(.x, na.rm = TRUE),
    min = ~min(.x, na.rm = TRUE),
    mean = ~mean(.x, na.rm = TRUE),
    first = ~first(na.omit(.x))
  )
  data <- data %>%
    group_by(id, sfseverity_highest) %>%
    mutate(
      !!as.symbol(var_x) := ifelse((DPSO > maxdx) | (DPSO < mindx), NA_real_, !!as.symbol(var_x)),
      !!as.symbol(var_y) := ifelse((DPSO > maxdy) | (DPSO < mindy), NA_real_, !!as.symbol(var_y))
    ) %>%
    arrange(desc(all_of(var_y))) %>%
    filter(
      !is.na(!!as.symbol(var_x)) | !is.na(!!as.symbol(var_y)),
      !is.infinite(!!as.symbol(var_x)) | !is.infinite(!!as.symbol(var_y))
    )
  if (var_x == "DPSO") {
    data <- data %>%
      filter(!is.na(!!as.symbol(var_y)), !is.infinite(!!as.symbol(var_y)),
             (DPSO <= maxdy) | (DPSO >= mindy))
  }
  if ((fun_x != "none") & (fun_y != "none")) {
    data <- data %>%
    summarise(
      across(var_x, list_funs[[fun_x]]),
      across(var_y, list_funs[[fun_y]])
    ) %>%
    filter(
      !is.na(!!as.symbol(var_x)) & !is.na(!!as.symbol(var_y)),
      !is.infinite(!!as.symbol(var_x)) & !is.infinite(!!as.symbol(var_y))
    )
  }
  namify <- function(str_name) {
    str_name %>%
      tolower() %>%
      str_replace_all("\\. ", "-") %>%
      str_replace_all("\\/", "-") %>%
      str_replace_all("\\| ", "") %>%
      str_replace_all("\\+ ", "-") %>%
      str_replace_all(" ", "-") %>%
      str_replace_all("\\.", "-") %>%
      str_replace_all("\\(", "") %>%
      str_replace_all("\\)", "") %>%
      str_replace_all("\\%", "pct") %>%
      str_replace_all("\\:", "") %>%
      return()
  }
  list_plotns <- fun_scatterit(data, var_x, var_y, log_x, log_y, pow)
  ggsave(list_plotns[[1]], filename = paste0(STR_PLOT_DIR_OTHER, namify(var_x), "_", namify(var_y), if(pow) "-regression" else "", ".svg"), width = INT_FIG_WIDTH, height = INT_FIG_HEIGHT)
  return(list_plotns)
}

monos <- names(tib_data_other)[grep("monocyte", names(tib_data_other), ignore.case = TRUE)]

list_var_x <- c(rep("Viral load", length(list_cytokines_all) + 2),
                c("Viral load", "Age", "Total Ig Spike", "Total Ig RBD", "DPSO", "SF Ratio"), c("DPSO"),
                rep("DPSO", length(list_cytokines_all)),
                c("CRP", "IL-10"),
                rep("GM-CSF", 7))
list_var_y <- c(list_cytokines_all, c("Total Ig Spike", "Total Ig RBD"),
                rep("IFNg ELISPOT", 6), c("Viral load"),
                list_cytokines_all,
                c("IL-6", "IL-6"),
                c(monos[grep("cd45", monos, ignore.case = TRUE)], "% Monocytes", monos[grep("hla-dr", monos, ignore.case = TRUE)]))
list_fun_x <- c(rep("max", length(list_cytokines_all) + 2),
                c("max", "max", "max", "max", "first", "first"), c("first"),
                rep("none", length(list_cytokines_all)),
                c("max", "max"),
                rep("max", 7))
list_fun_y <- c(rep("max", length(list_cytokines_all) + 2),
                rep("max", 6), c("max"),
                rep("none", length(list_cytokines_all)),
                c("max", "max"),
                rep("mean", 7))
list_log_x <- c(rep(TRUE, length(list_cytokines_all) + 2),
                c(TRUE, FALSE, TRUE, TRUE, FALSE, FALSE, FALSE),
                rep(FALSE, length(list_cytokines_all)),
                c(FALSE, TRUE),
                rep(TRUE, 7))
list_log_y <- c(rep(TRUE, length(list_cytokines_all) + 2),
                rep(FALSE, 6), c(TRUE),
                rep(TRUE, length(list_cytokines_all)),
                c(TRUE, TRUE),
                rep(FALSE, 4), rep(TRUE, 3))
list_mindx <- c(rep(-1, length(list_cytokines_all)), c(10, 10),
                c(-1, -1, 10, 10, -1, -1), c(-1),
                rep(-1, length(list_cytokines_all)),
                c(-1, -1),
                rep(-1, 7))
list_maxdx <- c(rep(30, length(list_cytokines_all)), c(300, 300),
                c(30, 300, 300, 300, 300, 300), c(300),
                rep(300, length(list_cytokines_all)),
                c(30, 30),
                rep(30, 7))
list_mindy <- c(rep(-1, length(list_cytokines_all) + 2),
                rep(5, 6), c(-1),
                rep(-1, length(list_cytokines_all)),
                c(-1, -1),
                rep(-1, 7))
list_maxdy <- c(rep(300, length(list_cytokines_all) + 2),
                rep(30, 6), c(30),
                rep(300, length(list_cytokines_all)),
                c(30, 30),
                rep(30, 7))

list_plotns <- mapply(fun_prepscatter,
       c(list_var_x, list_var_x),
       c(list_var_y, list_var_y),
       c(list_fun_x, list_fun_x),
       c(list_fun_y, list_fun_y),
       c(list_log_x, list_log_x),
       c(list_log_y, list_log_y),
       c(rep(FALSE, length(list_log_x)), rep(TRUE, length(list_log_x))),
       c(list_mindx, list_mindx),
       c(list_maxdx, list_maxdx),
       c(list_mindy, list_mindy),
       c(list_maxdy, list_maxdy),
       SIMPLIFY = FALSE)
tib_ns <- bind_rows(lapply(list_plotns, get_lists, 2))
list_plots <- lapply(list_plotns, get_lists, 1)
names(list_plots) <- mapply(
  function(x, y, z){paste0(x," vs ", y, ifelse(z, " Regression", ""))},
  list_var_x, list_var_y, c(rep(FALSE, length(list_var_x)), rep(TRUE, length(list_var_x))))

saveRDS(list_plots, paste0(STR_PLOT_DIR_OTHER, "scatter.rds"))
writexl::write_xlsx(tib_ns, paste0(STR_PLOT_DIR_OTHER, "scatter_ns.xlsx"))
```


```{r Miscellaneous - Plotting - Scatter - Mild/Severe}

fun_scatterit_ms <- function(data, str_x, str_y, logscale_x = FALSE, logscale_y = FALSE, pow = FALSE){
  fun_cytokine_title <- function(label) {
    label %>% str_replace("IFNa", "IFN\u03B1") %>%
      str_replace("IFNg", "IFN\u03B3") %>%
      str_replace("(Fa)$", "F\u03B1") %>%
      str_replace("(Ra)$", "R\u03B1") %>%
      str_replace("1a", "1\u03B1") %>%
      str_replace("1b", "1\u03B2") %>%
    return()
  }
  
  tib_ns <- data %>%
    group_by(sfseverity_highest) %>%
    select(sfseverity_highest, id) %>%
    unique() %>%
    summarise(ns = n()) %>%
    spread(sfseverity_highest, ns) %>%
    mutate(Study = paste0(fun_cytokine_title(str_x), " vs ", fun_cytokine_title(str_y))) %>%
    relocate(Study)

  plot_one <- data %>%
    ggplot(aes_string(x = paste0("`", str_x, "`"), y = paste0("`", str_y, "`"))) +
    theme_bw() +
    geom_point(aes_string(color = "sfseverity_highest")) +
    # Labels
    labs(title = paste0(fun_cytokine_title(str_x), " vs. ", fun_cytokine_title(str_y))) +
    ylab(fun_cytokine_title(str_y)) +
    xlab(fun_cytokine_title(str_x)) +
    # Colors
    scale_colour_manual(values = plotcolors()) +
    # Legend colors
    #guides(color = guide_legend(reverse = TRUE)) +
    guides(color = FALSE) +
    theme(axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5)) + 
    {if (logscale_x) scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
            labels = trans_format("log10", math_format(10^.x))) } +
    {if (logscale_x) annotation_logticks(sides = "b") } +
    {if (logscale_y) scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
            labels = trans_format("log10", math_format(10^.x))) } +
    {if (logscale_y) annotation_logticks(sides = "l") } +
    # Scatter plot
    {if (pow) geom_smooth(data = data %>% filter(sfseverity_highest %in% c("Severe", "Mild")), aes(color = sfseverity_highest), method = "lm", formula = y ~ poly(x, 1))} +#,
#                      method.args = list(family = gaussian(link = 'log'))) } +
    # Adding CI
    {if (pow) stat_poly_eq(
      data = data %>% filter(sfseverity_highest %in% c("Severe", "Mild")),
      aes(color = sfseverity_highest, label = paste(stat(p.value.label), stat(rr.label), sep = "*\", \"*")),
      formula = y ~ poly(x, 1),
      label.x = "right", label.y = "bottom", size = 3,
      parse = TRUE
      ) }
  return(list(plot_one, tib_ns))
}

fun_prepscatter_ms <- function(var_x, var_y, fun_x, fun_y, log_x, log_y, pow = FALSE,
                            mindx = -1, maxdx = 300, mindy = -1, maxdy = 300,
                            data = tib_data_other) {
  list_funs <- list(
    max = ~max(.x, na.rm = TRUE),
    min = ~min(.x, na.rm = TRUE),
    mean = ~mean(.x, na.rm = TRUE),
    first = ~first(na.omit(.x))
  )
  data <- data %>%
    group_by(id, sfseverity_highest) %>%
    mutate(
      !!as.symbol(var_x) := ifelse((DPSO > maxdx) | (DPSO < mindx), NA_real_, !!as.symbol(var_x)),
      !!as.symbol(var_y) := ifelse((DPSO > maxdy) | (DPSO < mindy), NA_real_, !!as.symbol(var_y))
    ) %>%
    arrange(desc(all_of(var_y))) %>%
    filter(
      !is.na(!!as.symbol(var_x)) | !is.na(!!as.symbol(var_y)),
      !is.infinite(!!as.symbol(var_x)) | !is.infinite(!!as.symbol(var_y))
    )
  if (var_x == "DPSO") {
    data <- data %>%
      filter(!is.na(!!as.symbol(var_y)), !is.infinite(!!as.symbol(var_y)),
             (DPSO <= maxdy) | (DPSO >= mindy))
  }
  if ((fun_x != "none") & (fun_y != "none")) {
    data <- data %>%
    summarise(
      across(var_x, list_funs[[fun_x]]),
      across(var_y, list_funs[[fun_y]])
    ) %>%
    filter(
      !is.na(!!as.symbol(var_x)) & !is.na(!!as.symbol(var_y)),
      !is.infinite(!!as.symbol(var_x)) & !is.infinite(!!as.symbol(var_y))
    )
  }
  namify <- function(str_name) {
    str_name %>%
      tolower() %>%
      str_replace_all("\\. ", "-") %>%
      str_replace_all("\\/", "-") %>%
      str_replace_all("\\| ", "") %>%
      str_replace_all("\\+ ", "-") %>%
      str_replace_all(" ", "-") %>%
      str_replace_all("\\.", "-") %>%
      str_replace_all("\\(", "") %>%
      str_replace_all("\\)", "") %>%
      str_replace_all("\\%", "pct") %>%
      str_replace_all("\\:", "") %>%
      return()
  }
  list_plotns <- fun_scatterit_ms(data, var_x, var_y, log_x, log_y, pow)
  ggsave(list_plotns[[1]], filename = paste0(STR_PLOT_DIR_OTHER, namify(var_x), "_", namify(var_y), if(pow) "-regression-ms" else "", ".svg"), width = INT_FIG_WIDTH, height = INT_FIG_HEIGHT)
  return(list_plotns)
}

list_var_x <- c(rep("DPSO", length(list_cytokines_all)))
list_var_y <- c(list_cytokines_all)
list_fun_x <- c(rep("none", length(list_cytokines_all)))
list_fun_y <- c(rep("none", length(list_cytokines_all)))
list_log_x <- c(rep(FALSE, length(list_cytokines_all)))
list_log_y <- c(rep(TRUE, length(list_cytokines_all)))
list_mindx <- c(rep(-1, length(list_cytokines_all)))
list_maxdx <- c(rep(300, length(list_cytokines_all)))
list_mindy <- c(rep(-1, length(list_cytokines_all)))
list_maxdy <- c(rep(300, length(list_cytokines_all)))

list_plotns <- mapply(fun_prepscatter_ms,
       list_var_x,
       list_var_y,
       list_fun_x,
       list_fun_y,
       list_log_x,
       list_log_y,
       rep(TRUE, length(list_log_x)),
       list_mindx,
       list_maxdx,
       list_mindy,
       list_maxdy,
       SIMPLIFY = FALSE)
tib_ns <- bind_rows(lapply(list_plotns, get_lists, 2))
list_plots <- lapply(list_plotns, get_lists, 1)
names(list_plots) <- mapply(
  function(x, y){paste0(x," vs ", y, " Regression (Mild/Severe)")},
  list_var_x, list_var_y)

saveRDS(list_plots, paste0(STR_PLOT_DIR_OTHER, "scatter_msreg.rds"))
```

```{r Scatter Severe Days}
c_levels <- c(sflevels()[1:2], c("Deceased"))
c_colors <- c(plotcolors()[1:2], c("#2a2c2d"))
names(c_colors) <- c_levels

tib_data_severe <- tib_data_other %>%
  filter(sfseverity_highest %in% c_levels) %>% 
  mutate(
#    `Severity Duration` = ifelse(severe_days == 0, NA_real_, severe_days),
    `Total Non-Mild Days` = ifelse(moderate_days == 0, NA_real_, moderate_days),
#    `Total Severity Score` = ifelse(moderate_severe_days == 0, NA_real_, moderate_severe_days),
    sfseverity_highest = factor(ifelse((death_date <= discharge_date) & !is.na(death_date) & !is.na(discharge_date), "Deceased", as.character(sfseverity_highest)),
                                levels = c_levels)
    )

fun_scatterit_severedays <- function(data, str_x, str_y, logscale_x = FALSE, logscale_y = FALSE, pow = FALSE){
  fun_cytokine_title <- function(label) {
    label %>% str_replace("IFNa", "IFN\u03B1") %>%
      str_replace("IFNg", "IFN\u03B3") %>%
      str_replace("(Fa)$", "F\u03B1") %>%
      str_replace("(Ra)$", "R\u03B1") %>%
      str_replace("1a", "1\u03B1") %>%
      str_replace("1b", "1\u03B2") %>%
    return()
  }
  
  tib_ns <- data %>%
    group_by(sfseverity_highest) %>%
    select(sfseverity_highest, id) %>%
    unique() %>%
    summarise(ns = n()) %>%
    spread(sfseverity_highest, ns) %>%
    mutate(Study = paste0(fun_cytokine_title(str_x), " vs ", fun_cytokine_title(str_y))) %>%
    relocate(Study)

  plot_one <- data %>%
    ggplot(aes_string(x = paste0("`", str_x, "`"), y = paste0("`", str_y, "`"))) +
    theme_bw() +
    geom_point(aes_string(color = "sfseverity_highest")) +
    # Labels
#    labs(title = paste0(fun_cytokine_title(str_x), " vs. ", fun_cytokine_title(str_y))) +
    labs(title = fun_cytokine_title(str_y)) +
    ylab(fun_cytokine_title(str_y)) +
    xlab(fun_cytokine_title(str_x)) +
    # Colors
    scale_colour_manual(values = c_colors) +
    # Legend colors
    #guides(color = guide_legend(reverse = TRUE)) +
    guides(color = FALSE) +
    theme(axis.title.y=element_text(size = INT_SIG_SIZE*4.5), axis.text.y = element_text(size = INT_SIG_SIZE*4), title = element_text(size = INT_SIG_SIZE*4.5)) + 
    {if (logscale_x) scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
            labels = trans_format("log10", math_format(10^.x))) } +
    {if (logscale_x) annotation_logticks(sides = "b") } +
    {if (logscale_y) scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
            labels = trans_format("log10", math_format(10^.x))) } +
    {if (logscale_y) annotation_logticks(sides = "l") } +
    # Scatter plot
    {if (pow) geom_smooth(method = "lm", formula = y ~ poly(x, 1))} +#,
#                      method.args = list(family = gaussian(link = 'log'))) } +
    # Adding CI
    {if (pow) stat_poly_eq(
      aes(label = paste(stat(p.value.label), stat(rr.label), sep = "*\", \"*")),
      formula = y ~ poly(x, 1),
      label.x = "right", label.y = "bottom", size = 3,
      parse = TRUE
      ) }
  return(list(plot_one, tib_ns))
}

fun_prepscatter_severedays <- function(var_x, var_y, fun_x, fun_y, log_x, log_y, pow = FALSE,
                            mindx = -1, maxdx = 300, mindy = -1, maxdy = 300,
                            data = tib_data_severe) {
  list_funs <- list(
    max = ~max(.x, na.rm = TRUE),
    min = ~min(.x, na.rm = TRUE),
    mean = ~mean(.x, na.rm = TRUE),
    first = ~first(na.omit(.x))
  )
  data <- data %>%
    group_by(id, sfseverity_highest) %>%
    mutate(
      !!as.symbol(var_x) := ifelse((DPSO > maxdx) | (DPSO < mindx), NA_real_, !!as.symbol(var_x)),
      !!as.symbol(var_y) := ifelse((DPSO > maxdy) | (DPSO < mindy), NA_real_, !!as.symbol(var_y))
    ) %>%
    arrange(desc(all_of(var_y))) %>%
    filter(
      !is.na(!!as.symbol(var_x)) | !is.na(!!as.symbol(var_y)),
      !is.infinite(!!as.symbol(var_x)) | !is.infinite(!!as.symbol(var_y))
    )
  if (var_x == "DPSO") {
    data <- data %>%
      filter(!is.na(!!as.symbol(var_y)), !is.infinite(!!as.symbol(var_y)),
             (DPSO <= maxdy) | (DPSO >= mindy))
  }
  if ((fun_x != "none") & (fun_y != "none")) {
    data <- data %>%
    summarise(
      across(var_x, list_funs[[fun_x]]),
      across(var_y, list_funs[[fun_y]])
    ) %>%
    filter(
      !is.na(!!as.symbol(var_x)) & !is.na(!!as.symbol(var_y)),
      !is.infinite(!!as.symbol(var_x)) & !is.infinite(!!as.symbol(var_y))
    )
  }
  namify <- function(str_name) {
    str_name %>%
      tolower() %>%
      str_replace_all("\\. ", "-") %>%
      str_replace_all("\\/", "-") %>%
      str_replace_all("\\| ", "") %>%
      str_replace_all("\\+ ", "-") %>%
      str_replace_all(" ", "-") %>%
      str_replace_all("\\.", "-") %>%
      str_replace_all("\\(", "") %>%
      str_replace_all("\\)", "") %>%
      str_replace_all("\\<", "") %>%
      return()
  }
  list_plotns <- fun_scatterit_severedays(data, var_x, var_y, log_x, log_y, pow)
  ggsave(list_plotns[[1]], filename = paste0(STR_PLOT_DIR_OTHER, namify(var_x), "_", namify(var_y), if(pow) "-regression" else "", ".svg"), width = INT_FIG_WIDTH, height = INT_FIG_HEIGHT)
  return(list_plotns)
}

# list_var_x <- c(rep("Severity Duration", length(list_cytokines_all) + 3))
# list_var_y <- c(list_cytokines_all, c("Total Ig Spike", "Total Ig RBD", "IFNg ELISPOT"))
# list_fun_x <- c(rep("first", length(list_cytokines_all) + 3))
# list_fun_y <- c(rep("max", length(list_cytokines_all) + 3))
# list_log_x <- c(rep(FALSE, length(list_cytokines_all) + 3))
# list_log_y <- c(rep(TRUE, length(list_cytokines_all) + 2), c(FALSE))
# list_mindx <- c(rep(-1, length(list_cytokines_all) + 3))
# list_maxdx <- c(rep(300, length(list_cytokines_all) + 3))
# list_mindy <- c(rep(-1, length(list_cytokines_all)), c(10, 10, 5))
# list_maxdy <- c(rep(30, length(list_cytokines_all)), c(300, 300, 30))
# 
# 
# list_plotns <- mapply(fun_prepscatter_severedays,
#        c(list_var_x, list_var_x),
#        c(list_var_y, list_var_y),
#        c(list_fun_x, list_fun_x),
#        c(list_fun_y, list_fun_y),
#        c(list_log_x, list_log_x),
#        c(list_log_y, list_log_y),
#        c(rep(FALSE, length(list_log_x)), rep(TRUE, length(list_log_x))),
#        c(list_mindx, list_mindx),
#        c(list_maxdx, list_maxdx),
#        c(list_mindy, list_mindy),
#        c(list_maxdy, list_maxdy),
#        SIMPLIFY = FALSE)
# tib_ns <- bind_rows(lapply(list_plotns, get_lists, 2))
# list_plots <- lapply(list_plotns, get_lists, 1)
# names(list_plots) <- mapply(
#   function(x, y, z){paste0(x," vs ", y, ifelse(z, " Regression", ""))},
#   list_var_x, list_var_y, c(rep(FALSE, length(list_var_x)), rep(TRUE, length(list_var_x))))
# 
# saveRDS(list_plots, paste0(STR_PLOT_DIR_OTHER, "scatter_severedays.rds"))
# writexl::write_xlsx(tib_ns, paste0(STR_PLOT_DIR_OTHER, "scatter_severedays_ns.xlsx"))


list_var_x <- c(rep("Total Non-Mild Days", length(list_cytokines_all) + 3))
list_var_y <- c(list_cytokines_all, c("Total Ig Spike", "Total Ig RBD", "IFNg ELISPOT"))
list_fun_x <- c(rep("first", length(list_cytokines_all) + 3))
list_fun_y <- c(rep("max", length(list_cytokines_all) + 3))
list_log_x <- c(rep(FALSE, length(list_cytokines_all) + 3))
list_log_y <- c(rep(TRUE, length(list_cytokines_all) + 2), c(FALSE))
list_mindx <- c(rep(-1, length(list_cytokines_all) + 3))
list_maxdx <- c(rep(300, length(list_cytokines_all) + 3))
list_mindy <- c(rep(-1, length(list_cytokines_all)), c(10, 10, 5))
list_maxdy <- c(rep(30, length(list_cytokines_all)), c(300, 300, 30))


list_plotns <- mapply(fun_prepscatter_severedays,
       c(list_var_x, list_var_x),
       c(list_var_y, list_var_y),
       c(list_fun_x, list_fun_x),
       c(list_fun_y, list_fun_y),
       c(list_log_x, list_log_x),
       c(list_log_y, list_log_y),
       c(rep(FALSE, length(list_log_x)), rep(TRUE, length(list_log_x))),
       c(list_mindx, list_mindx),
       c(list_maxdx, list_maxdx),
       c(list_mindy, list_mindy),
       c(list_maxdy, list_maxdy),
       SIMPLIFY = FALSE)
tib_ns <- bind_rows(lapply(list_plotns, get_lists, 2))
list_plots <- lapply(list_plotns, get_lists, 1)
names(list_plots) <- mapply(
  function(x, y, z){paste0(x," vs ", y, ifelse(z, " Regression", ""))},
  list_var_x, list_var_y, c(rep(FALSE, length(list_var_x)), rep(TRUE, length(list_var_x))))

saveRDS(list_plots, paste0(STR_PLOT_DIR_OTHER, "scatter_totalnonmilddays.rds"))
writexl::write_xlsx(tib_ns, paste0(STR_PLOT_DIR_OTHER, "scatter_totalnonmilddays_ns.xlsx"))

# list_var_x <- c(rep("Total Severity Score", length(list_cytokines_all) + 3))
# list_var_y <- c(list_cytokines_all, c("Total Ig Spike", "Total Ig RBD", "IFNg ELISPOT"))
# list_fun_x <- c(rep("first", length(list_cytokines_all) + 3))
# list_fun_y <- c(rep("max", length(list_cytokines_all) + 3))
# list_log_x <- c(rep(FALSE, length(list_cytokines_all) + 3))
# list_log_y <- c(rep(TRUE, length(list_cytokines_all) + 2), c(FALSE))
# list_mindx <- c(rep(-1, length(list_cytokines_all) + 3))
# list_maxdx <- c(rep(300, length(list_cytokines_all) + 3))
# list_mindy <- c(rep(-1, length(list_cytokines_all)), c(10, 10, 5))
# list_maxdy <- c(rep(30, length(list_cytokines_all)), c(300, 300, 30))
# 
# 
# list_plotns <- mapply(fun_prepscatter_severedays,
#   list_var_x,
#   list_var_y,
#   list_fun_x,
#   list_fun_y,
#   list_log_x,
#   list_log_y,
#   rep(TRUE, length(list_log_x)),
#   list_mindx,
#   list_maxdx,
#   list_mindy,
#   list_maxdy,
#   SIMPLIFY = FALSE)
# tib_ns <- bind_rows(lapply(list_plotns, get_lists, 2))
# list_plots <- lapply(list_plotns, get_lists, 1)
# names(list_plots) <- mapply(
#   function(x, y, z){paste0(x," vs ", y, ifelse(z, " Regression", ""))},
#   list_var_x, list_var_y, c(rep(FALSE, length(list_var_x)), rep(TRUE, length(list_var_x))))
# 
# saveRDS(list_plots, paste0(STR_PLOT_DIR_OTHER, "scatter_severityscore.rds"))
# writexl::write_xlsx(tib_ns, paste0(STR_PLOT_DIR_OTHER, "scatter_severityscore_ns.xlsx"))

```
